### 2018-03-20 FlairResearch/Paper.tex
Created things

\documentclass[twocolumn]{article}

\title{Evaluation}
\usepackage{graphicx}
\usepackage[margin=0.75in]{geometry}

\graphicspath{ {graphs/} }

\addtolength{\topmargin}{0.25in}
	\addtolength{\textheight}{-0.5in}

\begin{document}

\begin{center}
\section*{Empirical Evaluation}
\end{center}

\paragraph{•}
	Our evaluation looks compare our tool, Flair, against some of the top of the line Android security analysis tools. We have narrowed our focus on four other inter-application analysis tools: COVERT, DidFail, DIALDroid, and SEALANT.

	\subparagraph{Covert}
		Jianghao probably explained this already
	\subparagraph{DidFail}
		Jianghao probably explained this already

		\begin{figure}[h]
			\includegraphics[width=\linewidth]{DidfailBoxPlot}
			\caption{Figure 1. This is a graph which shows Didfail's analysis times.}
		\end{figure}

	\subparagraph{DIALDroid}
		DIALDroid is an inter-application ICC security analysis tool with four key operations: ICC Entry / Exit Point Extraction, DataFlow Analysis, Data Aggregation, and ICC Leak Calculation.[1] DIALDroid extracts models from a given application and performs static analysis to find any ICC exit or entry leaks present. Then the information on any leaks is stored in a MySQL relational database to be retrieved when requested by SQL queries. During the initial analysis stage DIALDroid configures the precision based on the length of the analysis. During the first five minutes of analysis DIALDroid uses a high precision algorithm to find ICC entry and exit leaks. After five minutes DIALDroid switches to a low precision algorithm that has a higher change of false negative. If the analysis runs for more than a given timeout, such as 15 minutes, DIALDroid abandons the analysis of that application altogether.
	\subparagraph{SEALANT}
		Here is some text explain the tool Sealant.
\paragraph*{}
	To test each of these tools we used Oracle VirtualBox to create virtual machines running Ubuntu 16.04. For each tool the virtual machine was given the minimum amount of memory that we found it would run on. Covert, DidFail, and Flair all were given 3GB of memory, SEALANT was given 6GB, and DIALDroid, by far the most memory intensive, was given 14GB. Throughout all the tests The CPU was kept consistent at four physical cores and 8 threads. We found this to be the best way of testing each tool. Each tool was given enough memory to run efficiently, but none were given so much as to have a clear advantage over any other.\\ 
	We ran each tool against seven bundles of applications. Each bundle contained 50 popular android application.

\end{document}

### 2018-03-20 FlairResearch/CovertBoxPlot.m

@@ -1,0 +1,46 @@
+%Read Data in
+Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
+itemNo=50;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,i) = Covert(n,i);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,51]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Covert Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 2500]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-20 FlairResearch/DidfailBoxPlot.m

@@ -1,0 +1,45 @@
+%Read Data in
+Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
+itemNo=30;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:itemNo
+        datap(n,i) = Didfail(n,i);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,31]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Didfail Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 4500]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-20 FlairResearch/FlairBoxPlot.m

@@ -1,0 +1,46 @@
+%Read Data in
+Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
+itemNo=50;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,i) = Flair(n,i);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,51]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Flair Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 250]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-20 FlairResearch/NewWithCovertDidfailFlair.m

@@ -1,0 +1,94 @@
+Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
+Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
+Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
+itemNo = 150;
+%init Matrix
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,(i-1)*3+1) = Covert(n,i);
+        %        Flair 3,6,9...
+        datap(n,(i-1)*3+3) = Flair(n,i);
+        if i<31
+           %        Didfail 2,5,8...
+            datap(n,(i-1)*3+2) = Didfail(n,i);
+        else
+            datap(n,(i-1)*3+2) = -105;
+        end
+        
+        
+    end
+end
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+    if mod(n1,3) == 1
+%        Covert 1,4,7...
+         pos(n1) = (n1-1)/3 + 1;
+    elseif mod(n1,3) == 2
+%        Didfail 2,5,8...
+        pos(n1) = (n1-2)/3+1 +0.25;
+    else
+        %        Flair 3,6,9...
+        pos(n1) =n1/3 + 0.5;
+    end
+end
+
+%boxplot(datap,g,'positions',pos);
+
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26);
+ % 
+ 
+ ax = gca;
+ ax.FontSize = 19;
+ 
+ ylim([-100 4200]);
+ yt = get(gca,'YTick');
+%set(gca,'YTickLabel', sprintf('%.4f',yt))
+  xlabel('Bundle Size(#Apps)','FontSize',32);
+  
+ylabel('AnalysisTime (Seconds)','FontSize',32);
+
+
+  xAxisPos = zeros(1,itemNo/3);
+  for n2 = 1:(itemNo/3) 
+      y = n2*3-2;
+      z = y+2;
+      xAxisPos(n2) = mean(pos(y:z));
+  end
+ set(gca, 'xtick', xAxisPos);
+
+
+ 
+  grey =  [0.5, 0.5, 0.5];
+  white = [1,1,1];
+ dark =  [0.1, 0.1, 0.1];
[…]

### 2018-03-20 FlairResearch/RunBundle3.sh

@@ -1,0 +1,255 @@
+rm -R ./SEALANT/Analyzer/Input
+rm -R ./DIALDroid/build/bundle3
+
+mkdir ./SEALANT/Analyzer/Input
+mkdir ./DIALDroid/build/bundle3
+
+#1
+cp ~/Desktop/AndroidAPKs/apk3/biz.gyrus.yaab_30.apk ./DIALDroid/build/bundle3/
+cp ~/Desktop/AndroidAPKs/apk3/biz.gyrus.yaab_30.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#2
+cp ~/Desktop/AndroidAPKs/apk3/com.elementarytoday.theia_5.apk ./DIALDroid/build/bundle3
+cp ~/Desktop/AndroidAPKs/apk3/com.elementarytoday.theia_5.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#3
+cp ~/Desktop/AndroidAPKs/apk3/org.zeitgeist.movement_25.apk ./DIALDroid/build/bundle3
+cp ~/Desktop/AndroidAPKs/apk3/org.zeitgeist.movement_25.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#4
+cp ~/Desktop/AndroidAPKs/apk3/fr.xgouchet.texteditor_19.apk ./DIALDroid/build/bundle3
+cp ~/Desktop/AndroidAPKs/apk3/fr.xgouchet.texteditor_19.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#5
+cp ~/Desktop/AndroidAPKs/apk3/de.k3b.android.toGoZip_6.apk ./DIALDroid/build/bundle3
+cp ~/Desktop/AndroidAPKs/apk3/de.k3b.android.toGoZip_6.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#6
+cp ~/Desktop/AndroidAPKs/apk3/app.varlorg.unote_7.apk ./DIALDroid/build/bundle3
+cp ~/Desktop/AndroidAPKs/apk3/app.varlorg.unote_7.apk ./SEALANT/Analyzer/Input
+   ./AndroidSecurityTest.sh bundle3
+
+#7
[…]

### 2018-03-20 FlairResearch/SEALANTBoxPlot.m

@@ -1,0 +1,46 @@
+%Read Data in
+Flair = xlsread('FlairResults.xlsx','SEALANT','K5:O54');
+itemNo=50;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,i) = Flair(i,n);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,51]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('SEALANT Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 4000]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-20 FlairResearch/Paper.tex
Changed the paper

@@
 \paragraph{•}
-	Our evaluation looks compare our tool, Flair, against some of the top of the line Android security analysis tools.
-We have narrowed our focus on four other inter-application analysis tools: COVERT, DidFail, DIALDroid, and SEALANT.
+	We tested Flair's performance in relation to the following questions:\\
+	\textbf{Question 1:} How does Flair compare to other inter-application communication analysis tools in respect to the amount of time it takes to analyze a bundle of applications?\\
+	\textbf{Question 2:} How does Flair compare to other tools with respect to the number of applications it fails to analyze?\\
+	\textbf{Question 3:} How accurately does Flair analyze vulnerabilities within applications when ran against a bundle of benchmark applications?\\
+	\textbf{Question 4:} How does Flair's accuracy in analyzing applicaions compare to other inter-application analysis tools?\\
 

### 2018-03-20 FlairResearch/Paper.tex
Worked on the paper some.

@@
 \begin{center}
-\section*{Empirical Evaluation}
+\section[1]{Empirical Evaluation}
 \end{center}
@@
 
+\subsection{Methods of Testing}
+\paragraph{•}
+	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
+We used seven bundles of popular presented in table 1 android applications, each with fifty applications, to answer Question 1 and Questions 2.
+We then used three bundles of benchmark bundles also presented in table 1 to answer Question 3 and Question 4.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{ |c c| }
+	\hline
+	Bundle & Apks\\
+	\hline
+	Android Bundle 1 & 50\\
+	Android Bundle 2 & 50\\
+	Android Bundle 3 & 50\\
+	Android Bundle 4 & 50\\
+	Android Bundle 5 & 50\\
+	Android Bundle 6 & 50\\
+	Android Bundle 7 & 50\\
+	Benchmark Bundle & XX\\
+	Benchmark Bundle & XX\\
+	Benchmark Bundle & XX\\
+	\hline
+\end{tabular}
+\end{center}
+\caption{Bundles used in analysis.}
+\label{table:1}
+\end{table}
+
+\paragraph{•}
+	Each of the bundles used to examine Question 1 and Question 2 were run incrimentally.
+Each test started with only one application from the bundle and the tool was run against it.
+Then another application was added and the tool was run against the new bundle of two applications.
+This process was repeated until all the applications from the specified bundle were added.
+Therefore, each test consisted of 50 consecutive runs of a tool, each consisting of one more application than the last.
+This was done to reflect how in a real life situation applications are added to a collection that is being checked for vulnerabilities.
+It is benficial for us to see how each tool performs when new applications are added to a bundle.
+To more accurate results we ran each tool against each bundle three times and used the averages from those runs for our data.
+\paragraph{•}
+	We gathered data for Question 1 by recording the time it tool each tool to analyze bundles of applications.
+We recorded the time each tool took for each successive run of a test.
+Hence, there was fifty recorded times for each test of a tool.
+The averages for each bundle were then entered into box plot graphs and evaluated.
+\paragraph{•}
+	To answer Question 2 we used error logs provided by eac tool.
+The tools provided a single error log file for each application that they failed to analyze.
+We then calculated the failure rate of each tool by:\\
+	\begin{center}
+		\(\frac{failed}{num}=FR\)
+	\end{center}
+	Where \textit{failed} is the number of error logs given by the tool, \textit{num} is the total number of applications run in the test, here it is 1250, and \textit{FR} is the failure rate for that tool in that test.
+The failure rates were recorded for each test and then averaged for each tool across all bundles.
+\paragraph{•}
+	\textbf{Here will go text explaining Question 3 proceedure.}
+\paragraph{•}
+	\textbf{Here will go text explaining Question 4 proceedure.}
+
+\subsection{Variables}
+\paragraph{•}
+	\textbf{Independent:} Our independent variables present in our test are as follows: (1) Tool used to analyze. (2) Specific bundle which the tool analyzed.\\
+	\textbf{Dependent:} The dependent variables in our study are as follows: (1) Time it takes for tool to analyze a bundle.
+(2) Number of applications that a tool fails to analyze.
+(3) The accuracy of the analysis.
+
+\subsection{Testing Enviroment}
+	All testing for Question 1 and Question 2 was done on virtual machines running within Oracle VirtualBox.
+Each of these machines was running Ubuntu 16.04 and had 8 processing threads clocked at 2.28 Ghz.
+The memory varied due to the fact that each tool had differing memory requirments.
+For Covert, Didfail, and Flair the machine was given 3 Gb of memory.
+SEALANT required more memory to run and was given 6 Gb.
+DIALDroid, the most memory intensive, was given 14 Gb.
+Since SEALANT and DIALDroid had much higher memory requirements than the other tools, we gave them lower limit of the amount of memory that they needed to run.
+We did this so that each tool would have enough memory to run efficiently, but the higher memory requirement tools did not have a clear advantage.
+In addtion, there was no swap space avaliable for any of the tools.
+
+\subsection{Threats to Validity}
+\paragraph{•}
+	\textbf{Innconsitant Runs:} Thought we ran all tests in isolated virtual machines, there still could have been issues realted to a run that is not consistant with the tools true performance.
+To minimize these affects we ran each tool against each bundle three times and took the averages.
+\paragraph{•}
+	\textbf{Interal issues:} Issues related to the structure and design of the tools themselves. We are not aware of any issues of this kind.
+\paragraph{•}
+	\textbf{Measurement Issues:} Issues related to the methods we used to record and analyze our data. We did not notice any issued related to this.
+
+\subsection{Results}
+Presumable would enter in results analysis here.
+
+\section[2]{Related Work}
+
 	\subparagraph{Covert}
@@
 		Jianghao probably explained this already
-
-		\begin{figure}[h]
-			\includegraphics[width=\linewidth]{DidfailBoxPlot}
-			\caption{Figure 1. This is a graph which shows Didfail's analysis times.}
-		\end{figure}
 
@@
 
+\section[3]{Conclusion}
+Here we will have a conclusion.
+
 \end{document}

### 2018-03-20 FlairResearch/DidfailBoxPlot.m
Changed the matlab files and graphs

@@ -30,7 +30,7 @@ ylabel('AnalysisTime (Seconds)','FontSize',26);
 title('Didfail Analysis','FontSize',32);
 
 %Set Y limits
-ylim([-100 4500]);
+ylim([-100 2500]);
 yt = get(gca,'YTick');
 
 %Gets the plots

### 2018-03-20 FlairResearch/FlairBoxPlot.m

@@ -31,7 +31,7 @@ ylabel('AnalysisTime (Seconds)','FontSize',26);
 title('Flair Analysis','FontSize',32);
 
 %Set Y limits
-ylim([-100 250]);
+ylim([-100 2500]);
 yt = get(gca,'YTick');
 
 %Gets the plots

### 2018-03-22 FlairResearch/RunBundle2.sh
Changed the graphs

@@ -1,256 +1,0 @@
-
-rm -R ./SEALANT/Analyzer/Input
-rm -R ./DIALDroid/build/bundle2
-
-mkdir ./SEALANT/Analyzer/Input
-mkdir ./DIALDroid/build/bundle2
-
-#1
-cp ~/Desktop/AndroidAPKs/apk2/app.varlorg.unote_7.apk ./DIALDroid/build/bundle2/
-cp ~/Desktop/AndroidAPKs/apk2/app.varlorg.unote_7.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#2
-cp ~/Desktop/AndroidAPKs/apk2/com.doomy.torch_11.apk ./DIALDroid/build/bundle2
-cp ~/Desktop/AndroidAPKs/apk2/com.doomy.torch_11.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#3
-cp ~/Desktop/AndroidAPKs/apk2/com.howeyc.spiped_3.apk ./DIALDroid/build/bundle2
-cp ~/Desktop/AndroidAPKs/apk2/com.howeyc.spiped_3.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#4
-cp ~/Desktop/AndroidAPKs/apk2/com.pikselbit.wrongpinshutdown_2.apk ./DIALDroid/build/bundle2
-cp ~/Desktop/AndroidAPKs/apk2/com.pikselbit.wrongpinshutdown_2.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#5
-cp ~/Desktop/AndroidAPKs/apk2/de.freewarepoint.whohasmystuff_26.apk ./DIALDroid/build/bundle2
-cp ~/Desktop/AndroidAPKs/apk2/de.freewarepoint.whohasmystuff_26.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#6
-cp ~/Desktop/AndroidAPKs/apk2/com.github.timnew.smartremotecontrol_1.apk ./DIALDroid/build/bundle2
-cp ~/Desktop/AndroidAPKs/apk2/com.github.timnew.smartremotecontrol_1.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle2
-
-#7
[…]

### 2018-03-22 FlairResearch/RunBundle3.sh

@@ -1,255 +1,0 @@
-rm -R ./SEALANT/Analyzer/Input
-rm -R ./DIALDroid/build/bundle3
-
-mkdir ./SEALANT/Analyzer/Input
-mkdir ./DIALDroid/build/bundle3
-
-#1
-cp ~/Desktop/AndroidAPKs/apk3/biz.gyrus.yaab_30.apk ./DIALDroid/build/bundle3/
-cp ~/Desktop/AndroidAPKs/apk3/biz.gyrus.yaab_30.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#2
-cp ~/Desktop/AndroidAPKs/apk3/com.elementarytoday.theia_5.apk ./DIALDroid/build/bundle3
-cp ~/Desktop/AndroidAPKs/apk3/com.elementarytoday.theia_5.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#3
-cp ~/Desktop/AndroidAPKs/apk3/org.zeitgeist.movement_25.apk ./DIALDroid/build/bundle3
-cp ~/Desktop/AndroidAPKs/apk3/org.zeitgeist.movement_25.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#4
-cp ~/Desktop/AndroidAPKs/apk3/fr.xgouchet.texteditor_19.apk ./DIALDroid/build/bundle3
-cp ~/Desktop/AndroidAPKs/apk3/fr.xgouchet.texteditor_19.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#5
-cp ~/Desktop/AndroidAPKs/apk3/de.k3b.android.toGoZip_6.apk ./DIALDroid/build/bundle3
-cp ~/Desktop/AndroidAPKs/apk3/de.k3b.android.toGoZip_6.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#6
-cp ~/Desktop/AndroidAPKs/apk3/app.varlorg.unote_7.apk ./DIALDroid/build/bundle3
-cp ~/Desktop/AndroidAPKs/apk3/app.varlorg.unote_7.apk ./SEALANT/Analyzer/Input
-   ./AndroidSecurityTest.sh bundle3
-
-#7
[…]

### 2018-03-22 FlairResearch/Paper.tex
Worked on paper

@@
 \subsection{Results}
+\onecolumn
+\begin{figure}[hb!]
+	\includegraphics[width=\textwidth]{CovertBoxPlot}
+	\label{figure:1}
+	\caption{Box plot graph showing Covert analysis times.}
+\end{figure}
+\begin{figure}[hb!]
+	\includegraphics[width=\textwidth]{DidfailBoxPlot}
+	\label{figure:2}
+	\caption{Box plot graph showing Didfail analysis times.}
+\end{figure}
+\begin{figure}[hb!]
+	\includegraphics[width=\textwidth]{DIALDroidBoxPlot}
+	\label{figure:3}
+	\caption{Box plot showing DIALDroid analysis times.}
+\end{figure}
+\begin{figure}[hb!]
+	\includegraphics[width=\textwidth]{SEALANTBoxPlot}
+	\label{figure:4}
+	\caption{Box plot showing SEALANT analysis times.}
+\end{figure}
+\begin{figure}[hb!]
+	\includegraphics[width=\textwidth]{FlairBoxPlot}
+	\label{figure:5}
+	\caption{Box plot showing Flair analysis times.}
+\end{figure}
+\twocolumn
 Presumable would enter in results analysis here.
@@
 		Here is some text explain the tool Sealant.
-\paragraph*{}
-	To test each of these tools we used Oracle VirtualBox to create virtual machines running Ubuntu 16.04.
-For each tool the virtual machine was given the minimum amount of memory that we found it would run on.
-Covert, DidFail, and Flair all were given 3GB of memory, SEALANT was given 6GB, and DIALDroid, by far the most memory intensive, was given 14GB.
-Throughout all the tests The CPU was kept consistent at four physical cores and 8 threads.
-We found this to be the best way of testing each tool.
-Each tool was given enough memory to run efficiently, but none were given so much as to have a clear advantage over any other.\\
-	We ran each tool against seven bundles of applications. Each bundle contained 50 popular android application.
 

### 2018-03-23 FlairResearch/Paper.tex
Changed some graphs. Worked on paper.

@@
 \usepackage[margin=0.75in]{geometry}
+\usepackage{subcaption}
+\usepackage{float}
+\usepackage{blindtext}
 
@@
 
+\section[1]{Related Work}
+	There are many existing tools that closely relate to Flair in their goals. We provide an overview of the most prevalent of those tools below:
+	\subparagraph{Covert}
+		Covert is a tool which allows for that analysing of inter-application vulnerabilities in android applications.
+It has been formulated to enable to analysis of bundles of applications.
+It has two main processes.
+The first is model extraction where the tool extracts models from the APK files, and the second is that formal analyzer which processes those models and presents any vulnerabilities in an xml file\cite{Covert}.
+	\subparagraph{DidFail}
+		Jianghao probably explained this already
+
+	\subparagraph{DIALDroid}
+		DIALDroid is an inter-application ICC security analysis tool with four key operations: ICC Entry / Exit Point Extraction, DataFlow Analysis, Data Aggregation, and ICC Leak Calculation\cite{DIALDroid}.
+DIALDroid extracts models from a given application and performs static analysis to find any ICC exit or entry leaks present.
+Then the information on any leaks is stored in a MySQL relational database to be retrieved via SQL queries.
+During the initial analysis stage DIALDroid changes the precision based on the length of the analysis.
+During the first five minutes of analysis DIALDroid uses a high precision algorithm to find ICC entry and exit leaks.
+After five minutes DIALDroid switches to a low precision algorithm that has a higher change of false negative.
+If the analysis runs for more than a given timeout, such as 15 minutes, DIALDroid abandons the analysis of that application altogether\cite{DIALDroid}.
+	\subparagraph{SEALANT}
+		SEALANT is an android security systems with the goal of both finding and preventing malicious android activity.
+It is composed of two tools: an analyzer and an interceptor.
+In this paper we focus only on the analyzer tool as it is closely related to our research.
+The analyzer works similarly to other ICC analysis tools.
+First, it extracts ICC paths from APK files.
+It then identifies vulnerable paths using formal analysis.
+Lastly, it entered in vulnerabilities into a list that will be used by the SEALANT interceptor tool.
+
 \begin{center}
-\section[1]{Empirical Evaluation}
+\section[2]{Empirical Evaluation}
 \end{center}
@@
 
-\subsection{Methods of Testing}
+\subsection{Methods of Testing} \label{methods}
 \paragraph{•}
@@
 \paragraph{•}
-	\textbf{Innconsitant Runs:} Thought we ran all tests in isolated virtual machines, there still could have been issues realted to a run that is not consistant with the tools true performance.
+	\textbf{Innconsitant Runs:} Though we ran all tests in isolated virtual machines, there still could have been issues realted to a run that is not consistant with the tools true performance.
 To minimize these affects we ran each tool against each bundle three times and took the averages.
@@
 
+\clearpage
+\newpage
+
 \subsection{Results}
+
+%Figure that represents the box plot graphs of all the Tools
+\begin{figure}[ht]
 \onecolumn
-\begin{figure}[hb!]
-	\includegraphics[width=\textwidth]{CovertBoxPlot}
+\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{CovertBoxPlot}
+		\caption{}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{DIALDroidBoxPlot}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{SEALANTBoxPlot}
+		\caption{}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{FlairBoxPlot}
+		\caption{}
+	\end{subfigure}
+
 	\label{figure:1}
-	\caption{Box plot graph showing Covert analysis times.}
+	\caption{Box plot graphs showing tool analysis times for various tools.}
 \end{figure}
-\begin{figure}[hb!]
-	\includegraphics[width=\textwidth]{DidfailBoxPlot}
+
+\twocolumn
+	%Average Analysis Time Graph
+	\begin{figure}
+		\includegraphics[width=\linewidth]{AverageGraph}
 		\label{figure:2}
-	\caption{Box plot graph showing Didfail analysis times.}
+		\caption{Average analysis times for tools.}
 	\end{figure}
-\begin{figure}[hb!]
-	\includegraphics[width=\textwidth]{DIALDroidBoxPlot}
-	\label{figure:3}
-	\caption{Box plot showing DIALDroid analysis times.}
-\end{figure}
-\begin{figure}[hb!]
-	\includegraphics[width=\textwidth]{SEALANTBoxPlot}
-	\label{figure:4}
-	\caption{Box plot showing SEALANT analysis times.}
-\end{figure}
-\begin{figure}[hb!]
-	\includegraphics[width=\textwidth]{FlairBoxPlot}
-	\label{figure:5}
-	\caption{Box plot showing Flair analysis times.}
-\end{figure}
-\twocolumn
-Presumable would enter in results analysis here.
 
-\section[2]{Related Work}
+	\subsection{Question 1:}
+		We first look to evaluate the analysis time of Flair in relation to Covert, DIALDroid, and SEALANT.
+The box plot graphs presented in Figure 1 show the spread of analysis times for each tool.
+This data is presented in accordance with Figure 2 which represents that average analysis time of all test run for all tools.
+These results show that Flair has a much smaller spread of analysis time across bundles, and much faster analysis times when analyzing bundles in an iterative fashion.
+Flair is able to analyze each application added to a bundle in a far faster since it only has to analyze that one application that was added, whereas the other tools analyze the entire bundle plus that additional application.\\
+		It is noticed in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much longer to analysis.
+This is most likely because SEALANT is built on top of Covert and runs Covert within its Analysis tool.
+In addition to Covert SEALANT also runs IC3 in its analyzer tool.
+The trend of covert is maintained in the data, but extra time is added with the addtion of the IC3.
+DIALDroid follows a trend which seems cause a great increase in time in the first few applications of a bundle.
+After those first few applications, DIALDroid increases at a much slower rate.
+Flair maintains a near horizontal trend far below the other average times.
 
-	\subparagraph{Covert}
-		Jianghao probably explained this already
-	\subparagraph{DidFail}
-		Jianghao probably explained this already
+	\subsection{Question 2:}
 
-	\subparagraph{DIALDroid}
-		DIALDroid is an inter-application ICC security analysis tool with four key operations: ICC Entry / Exit Point Extraction, DataFlow Analysis, Data Aggregation, and ICC Leak Calculation.[1] DIALDroid extracts models from a given application and performs static analysis to find any ICC exit or entry leaks present.
-Then the information on any leaks is stored in a MySQL relational database to be retrieved when requested by SQL queries.
-During the initial analysis stage DIALDroid configures the precision based on the length of the analysis.
-During the first five minutes of analysis DIALDroid uses a high precision algorithm to find ICC entry and exit leaks.
-After five minutes DIALDroid switches to a low precision algorithm that has a higher change of false negative.
-If the analysis runs for more than a given timeout, such as 15 minutes, DIALDroid abandons the analysis of that application altogether.
-	\subparagraph{SEALANT}
-		Here is some text explain the tool Sealant.
+		%Table for the Failure Rate of Tools
+		\begin{table}[h]
+		\begin{center}
+			\begin{tabular}{ |c c| }
+				\hline
+				Tool & Percentage Failed\\
+				\hline
+				Covert & 0\\
+				DIALDroid & 32.19\\
+				SEALANT & 0\\
+				Flair & 0\\
+				\hline
+			\end{tabular}		
+			\end{center}
+		\end{table}
+
+		To assess the rate of failure in the various tools we used the methods decribed in \ref{figure:1}
+
+	\subsection{Question 3:}
+		text
+	\subsection{Question 4:}
+		text
 

### 2018-03-23 FlairResearch/AveragesLineGraph.m

@@ -1,0 +1,29 @@
+X = xlsread('FlairResults.xlsx','Total Averages','A5:A54');
+CovertAverage=xlsread('FlairResults.xlsx','Total Averages','B5:B54');
+FlairAverage=xlsread('FlairResults.xlsx','Total Averages','D5:D54');
+SEALANTAverage=xlsread('FlairResults.xlsx','Total Averages','E5:E54');
+DIALDroidAverage=xlsread('FlairResults.xlsx','Total Averages','F5:F54');
+
+black=[0,0,0];
+darkgrey=[0.25,0.25,0.25];
+grey=[0.5,0.5,0.5];
+lightgrey=[0.75,0.75,0.75];
+
+plot(X,CovertAverage,'Color',black);
+hold on
+plot(X,FlairAverage,'Color',darkgrey);
+hold on
+plot(X,SEALANTAverage,'Color',grey);
+hold on
+plot(X,DIALDroidAverage,'--','Color',darkgrey);
+hold off
+
+legend({'Covert','Flair','SEALANT','DIALDroid'},'Location','northwest','FontSize',18);
+
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Average Analysis Time','FontSize',32);
+
+xlim([1,50]);
+ylim([0,2000]);

### 2018-03-23 FlairResearch/SEALANTBoxPlot.m

@@ -31,7 +31,7 @@ ylabel('AnalysisTime (Seconds)','FontSize',26);
 title('SEALANT Analysis','FontSize',32);
 
 %Set Y limits
-ylim([-100 4000]);
+ylim([-100 2500]);
 yt = get(gca,'YTick');
 
 %Gets the plots

### 2018-03-23 FlairResearch/Paper.tex
Worked on paper some..

@@
 	\subparagraph{Covert}
-		Covert is a tool which allows for that analysing of inter-application vulnerabilities in android applications.
+		Covert is a inter-application communication analysis tool which allows for that analysing of inter-application vulnerabilities in android applications.
 It has been formulated to enable to analysis of bundles of applications.
@@
 	\subparagraph{DidFail}
-		Jianghao probably explained this already
+		Didfail is a tool built off of another tool \textit{FlowDroid} \cite{Didfail}.
+Similarly to Covert, it allows for the analysis of bundles of applications instead of just single applications, which was an improvement over \textit{FlowDroid}.
+Didfail consists of two phases of analysis.
+The first phase contains the tools Epicc, Dare, Soot, and FlowDroid.
+The second phase contains only TaintFlows \cite{Didfail}.
+Unlike the other tools, Didfail is unable to identify privilege escalation vulnerabilities within applications.
 
@@
 	\textbf{Question 2:} How does Flair compare to other tools with respect to the number of applications it fails to analyze?\\
-	\textbf{Question 3:} How accurately does Flair analyze vulnerabilities within applications when ran against a bundle of benchmark applications?\\
-	\textbf{Question 4:} How does Flair's accuracy in analyzing applicaions compare to other inter-application analysis tools?\\
+	\textbf{Question 3:} How accurately does Flair analyze privilege escalation vulnerabilities within applications when ran against a bundle of benchmark applications?\\
+	\textbf{Question 4:} How does Flair's accuracy in analyzing privilege escalations compare to other inter-application communication analysis tools?\\
 
@@
 	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
-We used seven bundles of popular presented in table 1 android applications, each with fifty applications, to answer Question 1 and Questions 2.
-We then used three bundles of benchmark bundles also presented in table 1 to answer Question 3 and Question 4.
+We used seven bundles of popular applications presented in \ref{table:1} android applications, each with fifty applications, to answer Question 1 and Questions 2.
+We then used two bundles of benchmark bundles also presented in table 1 to answer Question 3 and Question 4.
 
@@
 	Android Bundle 7 & 50\\
-	Benchmark Bundle & XX\\
-	Benchmark Bundle & XX\\
-	Benchmark Bundle & XX\\
+	DroidBench2.0 & 3\textbf{(Not Final)}\\
+	ICC-Bench & 9\\
 	\hline
@@
 \paragraph{•}
-	Each of the bundles used to examine Question 1 and Question 2 were run incrimentally.
+	Each of the bundles used to examine Question 1 and Question 2 were run incrementally.
 Each test started with only one application from the bundle and the tool was run against it.
@@
 This process was repeated until all the applications from the specified bundle were added.
-Therefore, each test consisted of 50 consecutive runs of a tool, each consisting of one more application than the last.
-This was done to reflect how in a real life situation applications are added to a collection that is being checked for vulnerabilities.
-It is benficial for us to see how each tool performs when new applications are added to a bundle.
-To more accurate results we ran each tool against each bundle three times and used the averages from those runs for our data.
+Therefore, each test bundle consisted of 50 consecutive runs of a tool, each consisting of one more application than the last.
+This was done to reflect how in a real world situation applications are added to a collection that is being checked for vulnerabilities.
+It is beneficial for us to see how each tool performs when new applications are added to a bundle.
+To more obtain more accurate results we ran each tool against each bundle three times and used the averages from those runs in our data.
 \paragraph{•}
@@
 \paragraph{•}
-	To answer Question 2 we used error logs provided by eac tool.
+	To answer Question 2 we used error logs provided by each tool.
 The tools provided a single error log file for each application that they failed to analyze.
@@
 \paragraph{•}
-	\textbf{Here will go text explaining Question 3 proceedure.}
+
+	\textbf{Here will go text explaining Question 3 procedure.}
 \paragraph{•}
-	\textbf{Here will go text explaining Question 4 proceedure.}
+	\textbf{Here will go text explaining Question 4 procedure.}
 
@@
 
-\subsection{Testing Enviroment}
+\subsection{Testing Environment}
 	All testing for Question 1 and Question 2 was done on virtual machines running within Oracle VirtualBox.
 Each of these machines was running Ubuntu 16.04 and had 8 processing threads clocked at 2.28 Ghz.
-The memory varied due to the fact that each tool had differing memory requirments.
-For Covert, Didfail, and Flair the machine was given 3 Gb of memory.
-SEALANT required more memory to run and was given 6 Gb.
-DIALDroid, the most memory intensive, was given 14 Gb.
-Since SEALANT and DIALDroid had much higher memory requirements than the other tools, we gave them lower limit of the amount of memory that they needed to run.
+The memory varied due to the fact that each tool had differing memory requirements.
+For Covert, Didfail, and Flair the machine was given 3 GB of memory.
+SEALANT required more memory to run and was given 6 GB.
+DIALDroid, the most memory intensive, was given 14 GB.
+Since SEALANT and DIALDroid had much higher memory requirements than the other tools, we gave them the lower limit of the amount of memory that they needed to run.
 We did this so that each tool would have enough memory to run efficiently, but the higher memory requirement tools did not have a clear advantage.
-In addtion, there was no swap space avaliable for any of the tools.
+In addition, there was no swap space available for any of the tools.
 
@@
 \paragraph{•}
-	\textbf{Innconsitant Runs:} Though we ran all tests in isolated virtual machines, there still could have been issues realted to a run that is not consistant with the tools true performance.
+	\textbf{Inconsistent Runs:} Though we ran all tests in isolated virtual machines, there still could have been issues related to a run that is not consistent with the tools true performance.
 To minimize these affects we ran each tool against each bundle three times and took the averages.
 \paragraph{•}
-	\textbf{Interal issues:} Issues related to the structure and design of the tools themselves. We are not aware of any issues of this kind.
+	\textbf{Internal issues:} Issues related to the structure and design of the tools themselves. We are not aware of any issues of this kind.
 \paragraph{•}
@@
 In addition to Covert SEALANT also runs IC3 in its analyzer tool.
-The trend of covert is maintained in the data, but extra time is added with the addtion of the IC3.
+The trend of covert is maintained in the data, but extra time is added with the addition of the IC3.
 DIALDroid follows a trend which seems cause a great increase in time in the first few applications of a bundle.
 After those first few applications, DIALDroid increases at a much slower rate.
+Didfail's analysis times grows far faster than any of the other tools.
+Though it is not presented in \ref{figure:2}, Didfail fails to make it all the way to fifty applications.
+It could only get to thirty applications before failing to analyze any bundle that was larger.
 Flair maintains a near horizontal trend far below the other average times.
@@
 				SEALANT & 0\\
+				Didfail & 0\\
 				Flair & 0\\
@@
 			\end{center}
+			\label{table:2}
+			\caption{Rate of Failure for tools.}
 		\end{table}
 
-		To assess the rate of failure in the various tools we used the methods decribed in \ref{figure:1}
+		To assess the rate of failure in the various tools we used the methods described in \ref{methods} to find the percentage of applications in each test which failed.
+The data which was collected is presented in \ref{table:2}.
+This data shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{32.19 percent\textbf{(NOT FINAL NUMBER)}} of applications on average across all runs.
+This was primarily because DIALDroid would attempt to allocate more than our allotted 14 GB of memory, which was more than twice that allocated to any of the other tools.
+SEALANT, Covert, Didfail, and Flair all were able to run without any memory issues with far less memory.
+Therefore, Flair is able to analyze applications as reliably in terms of failure rate as well as SEALANT, Covert, and Didfail, while analyzing applications more reliably than DIALDroid.
 

### 2018-03-23 FlairResearch/AveragesLineGraph.m

@@ -3,6 +3,8 @@ CovertAverage=xlsread('FlairResults.xlsx','Total Averages','B5:B54');
 FlairAverage=xlsread('FlairResults.xlsx','Total Averages','D5:D54');
 SEALANTAverage=xlsread('FlairResults.xlsx','Total Averages','E5:E54');
 DIALDroidAverage=xlsread('FlairResults.xlsx','Total Averages','F5:F54');
+DidfailAverage=xlsread('FlairResults.xlsx','Total Averages','C5:C34');
+DIALDroidFitCurve=fit(X,DIALDroidAverage,'poly8','Normalize','on');
 
 black=[0,0,0];
 darkgrey=[0.25,0.25,0.25];
@@ -16,9 +18,13 @@ hold on
 plot(X,SEALANTAverage,'Color',grey);
 hold on
 plot(X,DIALDroidAverage,'--','Color',darkgrey);
+hold on
+plot(DidfailAverage,'-.','Color',grey);
+hold on
+plot(X,DIALDroidFitCurve,'Color','red');
 hold off
 
-legend({'Covert','Flair','SEALANT','DIALDroid'},'Location','northwest','FontSize',18);
+legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
 
 %Set labels
 xlabel('Bundle Size(#Apps)','FontSize',26);

### 2018-03-23 FlairResearch/Paper.tex
Edited some of the paper

@@
 	\subparagraph{Covert}
-		Covert is a inter-application communication analysis tool which allows for that analysing of inter-application vulnerabilities in android applications.
-It has been formulated to enable to analysis of bundles of applications.
+		Covert is a inter-application communication analysis tool which allows for the analyzing of inter-application vulnerabilities in android applications.
+It has been formulated to enable analysis of bundles of applications.
 It has two main processes.
@@
 		Didfail is a tool built off of another tool \textit{FlowDroid} \cite{Didfail}.
-Similarly to Covert, it allows for the analysis of bundles of applications instead of just single applications, which was an improvement over \textit{FlowDroid}.
+Similar to Covert, it allows for the analysis of bundles of applications instead of just single applications, which was an improvement over \textit{FlowDroid}.
 Didfail consists of two phases of analysis.
@@
 During the first five minutes of analysis DIALDroid uses a high precision algorithm to find ICC entry and exit leaks.
-After five minutes DIALDroid switches to a low precision algorithm that has a higher change of false negative.
+After five minutes, DIALDroid switches to a low precision algorithm that has a higher chance of false negative.
 If the analysis runs for more than a given timeout, such as 15 minutes, DIALDroid abandons the analysis of that application altogether\cite{DIALDroid}.
@@
 It then identifies vulnerable paths using formal analysis.
-Lastly, it entered in vulnerabilities into a list that will be used by the SEALANT interceptor tool.
+Lastly, it enters the identified vulnerabilities into a list that will be used by the SEALANT interceptor tool.
 
@@
 	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
-We used seven bundles of popular applications presented in \ref{table:1} android applications, each with fifty applications, to answer Question 1 and Questions 2.
+We used seven bundles of popular applications presented in table 1 android applications, each with fifty applications, to answer Question 1 and Questions 2.
 We then used two bundles of benchmark bundles also presented in table 1 to answer Question 3 and Question 4.
@@
 \paragraph{•}
-	We gathered data for Question 1 by recording the time it tool each tool to analyze bundles of applications.
+	We gathered data for Question 1 by recording the time it took each tool to analyze bundles of applications.
 We recorded the time each tool took for each successive run of a test.
@@
 The box plot graphs presented in Figure 1 show the spread of analysis times for each tool.
-This data is presented in accordance with Figure 2 which represents that average analysis time of all test run for all tools.
+This data is presented in accordance with Figure 2 which represents the average analysis time of all tests run for all tools.
 These results show that Flair has a much smaller spread of analysis time across bundles, and much faster analysis times when analyzing bundles in an iterative fashion.
-Flair is able to analyze each application added to a bundle in a far faster since it only has to analyze that one application that was added, whereas the other tools analyze the entire bundle plus that additional application.\\
-		It is noticed in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much longer to analysis.
+Flair is able to analyze each application added to a bundle far faster since it only has to analyze the one application that was added, whereas the other tools analyze the entire bundle plus an additional application.\\
+		It is noticed in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much greater analysis times.
 This is most likely because SEALANT is built on top of Covert and runs Covert within its Analysis tool.
@@
 The trend of covert is maintained in the data, but extra time is added with the addition of the IC3.
-DIALDroid follows a trend which seems cause a great increase in time in the first few applications of a bundle.
+DIALDroid follows a trend which appears to cause a great increase in time during the first few applications of a bundle.
 After those first few applications, DIALDroid increases at a much slower rate.

### 2018-03-24 FlairResearch/Paper.tex
Edited the paper. Made changes to related work, Research Quesions, and results sections.

@@
 	\subparagraph{Covert}
-		Covert is a inter-application communication analysis tool which allows for the analyzing of inter-application vulnerabilities in android applications.
-It has been formulated to enable analysis of bundles of applications.
-It has two main processes.
-The first is model extraction where the tool extracts models from the APK files, and the second is that formal analyzer which processes those models and presents any vulnerabilities in an xml file\cite{Covert}.
+		Covert is a tool for the compositional analysis of inter-application communication in Android.
+It allows for the anaylsis of both single applications and bundles of applications.
+It extracts the source code from each application, extracts communication and security information, and runs formal anaysis on that information to identify any inter-app vulnerabilities.\cite{Covert}.
 	\subparagraph{DidFail}
-		Didfail is a tool built off of another tool \textit{FlowDroid} \cite{Didfail}.
-Similar to Covert, it allows for the analysis of bundles of applications instead of just single applications, which was an improvement over \textit{FlowDroid}.
-Didfail consists of two phases of analysis.
-The first phase contains the tools Epicc, Dare, Soot, and FlowDroid.
-The second phase contains only TaintFlows \cite{Didfail}.
-Unlike the other tools, Didfail is unable to identify privilege escalation vulnerabilities within applications.
-
+		Didfail is an Android security system built on \textit{FlowDroid} and \textit{Epicc} focused on identifing both inter an intra-compnent vulnerabilities in bundles and individual applications.
+Didfail first identifies what communications allowed by each individual application.
+It then analyzes these possible communication to determine any vulnerabilties that may be present in the bundle or application.\cite{Didfail}
 	\subparagraph{DIALDroid}
-		DIALDroid is an inter-application ICC security analysis tool with four key operations: ICC Entry / Exit Point Extraction, DataFlow Analysis, Data Aggregation, and ICC Leak Calculation\cite{DIALDroid}.
-DIALDroid extracts models from a given application and performs static analysis to find any ICC exit or entry leaks present.
-Then the information on any leaks is stored in a MySQL relational database to be retrieved via SQL queries.
-During the initial analysis stage DIALDroid changes the precision based on the length of the analysis.
-During the first five minutes of analysis DIALDroid uses a high precision algorithm to find ICC entry and exit leaks.
-After five minutes, DIALDroid switches to a low precision algorithm that has a higher chance of false negative.
-If the analysis runs for more than a given timeout, such as 15 minutes, DIALDroid abandons the analysis of that application altogether\cite{DIALDroid}.
+		DIALDroid is an inter-application ICC security analysis system aimed at the analysis of extremely large bundles of applications.
+It identifies ICC leaks and privelege escalations within large bundles of applications.
+DIALDroid extracts permisions and possible inter-component communications from the APK files and then analyzes that extracted information.
+This analysis' percision is varies based on the time the application takes to complete.
+If the analysis of an application is not complete in a specified time limit, DIALDroid switches to a low precision analysis.
+If the low precision analysis does not complete within another specified time limit, the analysis is abandoned altogether.
+After the analysis of all applications in a bundle, the results are stored in a MySQL database to be retrieved when requested.\cite{DIALDroid}.
 	\subparagraph{SEALANT}
-		SEALANT is an android security systems with the goal of both finding and preventing malicious android activity.
+		SEALANT is an android security system with the goal of both finding and preventing malicious android activity.
 It is composed of two tools: an analyzer and an interceptor.
@@
 	We tested Flair's performance in relation to the following questions:\\
-	\textbf{Question 1:} How does Flair compare to other inter-application communication analysis tools in respect to the amount of time it takes to analyze a bundle of applications?\\
-	\textbf{Question 2:} How does Flair compare to other tools with respect to the number of applications it fails to analyze?\\
-	\textbf{Question 3:} How accurately does Flair analyze privilege escalation vulnerabilities within applications when ran against a bundle of benchmark applications?\\
-	\textbf{Question 4:} How does Flair's accuracy in analyzing privilege escalations compare to other inter-application communication analysis tools?\\
+	\textbf{RQ1:} How does Flair compare to other inter-application communication analysis tools in respect to the amount of time it takes to analyze a bundle of applications?\\
+	\textbf{RQ2:} How accurately does Flair analyze privilege escalation vulnerabilities within applications when ran against a bundle of benchmark applications?\\
+	\textbf{RQ3:} How does Flair's accuracy in analyzing privilege escalations compare to other inter-application communication analysis tools?\\
 
@@
 	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
-We used seven bundles of popular applications presented in table 1 android applications, each with fifty applications, to answer Question 1 and Questions 2.
-We then used two bundles of benchmark bundles also presented in table 1 to answer Question 3 and Question 4.
+We used seven bundles of popular applications presented in table 1, each with fifty applications, to answer RQ1 and RQ2.
+We then used two bundles of benchmark bundles also presented in table 1 to answer RQ3 and RQ4.
 
@@
 \paragraph{•}
-	Each of the bundles used to examine Question 1 and Question 2 were run incrementally.
-Each test started with only one application from the bundle and the tool was run against it.
-Then another application was added and the tool was run against the new bundle of two applications.
-This process was repeated until all the applications from the specified bundle were added.
-Therefore, each test bundle consisted of 50 consecutive runs of a tool, each consisting of one more application than the last.
-This was done to reflect how in a real world situation applications are added to a collection that is being checked for vulnerabilities.
-It is beneficial for us to see how each tool performs when new applications are added to a bundle.
-To more obtain more accurate results we ran each tool against each bundle three times and used the averages from those runs in our data.
+	Each test we ran to examine RQ1 was incrimental in nature.
+A shell script was utilized to copy each application from a given bundle into a specific input directiory.
+The shell script would then call a tool to be run against that input directory.
+Each application from a given bundle was copied one by one into the input directory, and the tool was run after each application was copied.
+This resulted in each test for a given bundle and tool to have 50 total runs.
+The order in which the bundles were copied into the input directories of each tool remained constant allowing the times outputed to be compared directly.
 \paragraph{•}
-	We gathered data for Question 1 by recording the time it took each tool to analyze bundles of applications.
-We recorded the time each tool took for each successive run of a test.
-Hence, there was fifty recorded times for each test of a tool.
-The averages for each bundle were then entered into box plot graphs and evaluated.
-\paragraph{•}
-	To answer Question 2 we used error logs provided by each tool.
-The tools provided a single error log file for each application that they failed to analyze.
-We then calculated the failure rate of each tool by:\\
+	To investigate RQ1 we ran the test described above and recorded the times it for the tools to analyze the bundles.
+At every step in the iteritive process the time was recorded before the tool was run against the input directory and after the analysis was completed.
+These times were then recorded into a CSV file.
+Each test outputed its times to a single CSV file and the times from all tests were combined into a master spreadsheet.
+These times were translated into graphs and are presented later in this paper.\\
+
+	In addition to analyzing the time it took each tool to analyze the bundles.
+We also noticed that DIALDroid would fail to analyze some applications.
+Each time it would fail to analyze an application it would output an error log file.
+After each test we would calculate the failure rate with the following calculation:\\
 	\begin{center}
@@
 	Where \textit{failed} is the number of error logs given by the tool, \textit{num} is the total number of applications run in the test, here it is 1250, and \textit{FR} is the failure rate for that tool in that test.
-The failure rates were recorded for each test and then averaged for each tool across all bundles.
+These failure rates were recorded and averaged.
+We did not notice any of the other tools failing to analyze applications during our tests.
 \paragraph{•}
 
-	\textbf{Here will go text explaining Question 3 procedure.}
+	\textbf{Here will go text explaining RQ3 procedure.}
 \paragraph{•}
@@
 \subsection{Testing Environment}
-	All testing for Question 1 and Question 2 was done on virtual machines running within Oracle VirtualBox.
+	All testing for Question 1 and RQ2 was done on virtual machines running within Oracle VirtualBox.
 Each of these machines was running Ubuntu 16.04 and had 8 processing threads clocked at 2.28 Ghz.
@@
 %Figure that represents the box plot graphs of all the Tools
-\begin{figure}[ht]
-\onecolumn
+\begin{figure*}[!ht]
+
 \centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{CovertBoxPlot}
-		\caption{}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{DIALDroidBoxPlot}
-		\caption{}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{SEALANTBoxPlot}
-		\caption{}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{FlairBoxPlot}
-		\caption{}
-	\end{subfigure}
-
+	\includegraphics[width=\linewidth]{BoxPlotGraph}
 	\label{figure:1}
 	\caption{Box plot graphs showing tool analysis times for various tools.}
-\end{figure}
+\end{figure*}
 
-\twocolumn
 	%Average Analysis Time Graph
-	\begin{figure}
+	\begin{figure}[H]
 		\includegraphics[width=\linewidth]{AverageGraph}
@@
 
-	\subsection{Question 1:}
+	\subsection{RQ1:}
 		We first look to evaluate the analysis time of Flair in relation to Covert, DIALDroid, and SEALANT.
@@
 
-	\subsection{Question 2:}
+	\subsection{RQ2:}
 
@@
 
-	\subsection{Question 3:}
+	\subsection{RQ3:}
 		text

### 2018-03-26 FlairResearch/Paper.tex
Did some things

@@
 	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
-We used seven bundles of popular applications presented in table 1, each with fifty applications, to answer RQ1 and RQ2.
-We then used two bundles of benchmark bundles also presented in table 1 to answer RQ3 and RQ4.
+We used seven bundles of popular applications presented in table 1, each with fifty applications, to answer RQ1.
+We then used two bundles of benchmark bundles also presented in table 1 to answer RQ2 and RQ3.
 
@@
 \paragraph{•}
-	Each test we ran to examine RQ1 was incrimental in nature.
-A shell script was utilized to copy each application from a given bundle into a specific input directiory.
+	Each test we ran to examine RQ1 was incremental in nature.
+A shell script was utilized to copy each application from a given bundle into a specific input directory.
 The shell script would then call a tool to be run against that input directory.
@@
 This resulted in each test for a given bundle and tool to have 50 total runs.
-The order in which the bundles were copied into the input directories of each tool remained constant allowing the times outputed to be compared directly.
+The order in which the bundles were copied into the input directories of each tool remained constant allowing the times outputted to be compared directly.
 \paragraph{•}
-	To investigate RQ1 we ran the test described above and recorded the times it for the tools to analyze the bundles.
-At every step in the iteritive process the time was recorded before the tool was run against the input directory and after the analysis was completed.
-These times were then recorded into a CSV file.
-Each test outputed its times to a single CSV file and the times from all tests were combined into a master spreadsheet.
+	To investigate RQ1 we ran the test described above and recorded the time it took for the tools to analyze the bundles.
+At every step in the iterative process the time was recorded before the tool was run against the input directory and after the analysis was completed.
+These times were then written to a CSV file.
+Each test outputted its times to a single CSV file and the times from all tests were then combined into a master spreadsheet.
 These times were translated into graphs and are presented later in this paper.\\
-
 	In addition to analyzing the time it took each tool to analyze the bundles.
@@
 	\end{center}
-	Where \textit{failed} is the number of error logs given by the tool, \textit{num} is the total number of applications run in the test, here it is 1250, and \textit{FR} is the failure rate for that tool in that test.
+	Where \textit{failed} is the number of error logs given by the tool, \textit{num} is the total number of applications run in the test, 1250, and \textit{FR} is the failure rate  in that test.
 These failure rates were recorded and averaged.
@@
 DIALDroid, the most memory intensive, was given 14 GB.
-Since SEALANT and DIALDroid had much higher memory requirements than the other tools, we gave them the lower limit of the amount of memory that they needed to run.
-We did this so that each tool would have enough memory to run efficiently, but the higher memory requirement tools did not have a clear advantage.
-In addition, there was no swap space available for any of the tools.
-
+These memory amounts were established by examining how much memory was allocated for each tool.
+The tools were each run with an excess of memory avaliable and then it was observed how much memory they each used.
+The tools were then given the amount of memory that each was observed to have used.
 \subsection{Threats to Validity}
@@
 It could only get to thirty applications before failing to analyze any bundle that was larger.
-Flair maintains a near horizontal trend far below the other average times.
-
-	\subsection{RQ2:}
-
-		%Table for the Failure Rate of Tools
-		\begin{table}[h]
-		\begin{center}
-			\begin{tabular}{ |c c| }
-				\hline
-				Tool & Percentage Failed\\
-				\hline
-				Covert & 0\\
-				DIALDroid & 32.19\\
-				SEALANT & 0\\
-				Didfail & 0\\
-				Flair & 0\\
-				\hline
-			\end{tabular}		
-			\end{center}
-			\label{table:2}
-			\caption{Rate of Failure for tools.}
-		\end{table}
+Flair maintains a near horizontal trend far below the other average times.\\
 
 		To assess the rate of failure in the various tools we used the methods described in \ref{methods} to find the percentage of applications in each test which failed.
-The data which was collected is presented in \ref{table:2}.
-This data shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{32.19 percent\textbf{(NOT FINAL NUMBER)}} of applications on average across all runs.
+The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{32.19 percent\textbf{(NOT FINAL NUMBER)}} of applications on average across all runs.
 This was primarily because DIALDroid would attempt to allocate more than our allotted 14 GB of memory, which was more than twice that allocated to any of the other tools.

### 2018-03-26 FlairResearch/NewWithCovertDidfailFlair.m

@@ -11,16 +11,16 @@ for  n=1:5
         %        Covert 1,6,11...
         datap(n,(i-1)*5+1) = Covert(n,i);
         %        Flair 3,8,13...
-        datap(n,(i-1)*5+3) = Flair(n,i);
+        datap(n,(i-1)*5+2) = Flair(n,i);
         %       SEALANT 4,9,14
         datap(n,(i-1)*5+4) = SEALANT(i,n);
         %       DIALDroid 5,10,15
         datap(n,(i-1)*5+5) = DIALDroid(i,n);
         if i<31
            %        Didfail 2,7,12...
-            datap(n,(i-1)*5+2) = Didfail(n,i);
+            datap(n,(i-1)*5+3) = Didfail(n,i);
         else
-            datap(n,(i-1)*5+2) = -105;
+            datap(n,(i-1)*5+3) = -105;
         end
         
         
@@ -74,14 +74,13 @@ ylabel('AnalysisTime (Seconds)','FontSize',32);
 
 xticks([10,20,30,40,50]);
 xticklabels({'10','20','30','40','50'});
-xlim([0,52]);
-
- 
-  grey =  [0.5, 0.5, 0.5];
-  lightgrey=[0.75,0.75,0.75];
-  darkgrey=[0.25,0.25,0.25];
+xlim([0,50.75]);
+                                                                                                                                                                                                                                                                                                                                                                         
+  red =  [0.75, 0, 0];
+  blue=[0,0,0.75];
+  green=[0,0.75,0];
   white = [1,1,1];
- dark =  [0.1, 0.1, 0.1];
+ dark =  [0, 0, 0];
  lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
  set(lines, 'Color', 'k');
 
@@ -90,16 +89,20 @@ xlim([0,52]);
    for j=1:length(h)
        x = mod(j,5);
        if x == 1
-           boxcolor = dark;
+           %Flair
+           boxcolor = white;
        elseif x==2
-           boxcolor = grey;
+           %Didfail
+           boxcolor = red;
        elseif x==3
            %Covert
-           boxcolor = white;
+           boxcolor = dark;
        elseif x==4
-           boxcolor = darkgrey;
+           %DIALDroid
+           boxcolor = blue;
        else
-           boxcolor = lightgrey;
+           %Sealant
[…]

### 2018-03-27 FlairResearch/Paper.tex
Did some graph stuff

@@
 Flair is able to analyze each application added to a bundle far faster since it only has to analyze the one application that was added, whereas the other tools analyze the entire bundle plus an additional application.\\
-		It is noticed in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much greater analysis times.
+		It is shown in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much greater analysis times.
 This is most likely because SEALANT is built on top of Covert and runs Covert within its Analysis tool.

### 2018-03-27 FlairResearch/AveragesLineGraph.m

@@ -4,7 +4,6 @@ FlairAverage=xlsread('FlairResults.xlsx','Total Averages','D5:D54');
 SEALANTAverage=xlsread('FlairResults.xlsx','Total Averages','E5:E54');
 DIALDroidAverage=xlsread('FlairResults.xlsx','Total Averages','F5:F54');
 DidfailAverage=xlsread('FlairResults.xlsx','Total Averages','C5:C34');
-DIALDroidFitCurve=fit(X,DIALDroidAverage,'poly8','Normalize','on');
 
 black=[0,0,0];
 darkgrey=[0.25,0.25,0.25];
@@ -20,16 +19,13 @@ hold on
 plot(X,DIALDroidAverage,'--','Color',darkgrey);
 hold on
 plot(DidfailAverage,'-.','Color',grey);
-hold on
-plot(X,DIALDroidFitCurve,'Color','red');
 hold off
 
 legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
 
 %Set labels
-xlabel('Bundle Size(#Apps)','FontSize',26);
-ylabel('AnalysisTime (Seconds)','FontSize',26);
-title('Average Analysis Time','FontSize',32);
+xlabel('Bundle Size(#Apps)','FontSize',24);
+ylabel('AnalysisTime (Seconds)','FontSize',24);
 
 xlim([1,50]);
-ylim([0,2000]);
+ylim([-100,4000]);

### 2018-03-27 FlairResearch/NewWithCovertDidfailFlair.m

@@ -56,7 +56,7 @@ end
  ax = gca;
  ax.FontSize = 19;
  
- ylim([-100 4200]);
+ ylim([-100 4000]);
  yt = get(gca,'YTick');
 %set(gca,'YTickLabel', sprintf('%.4f',yt))
   xlabel('Bundle Size(#Apps)','FontSize',32);
@@ -77,8 +77,8 @@ xticklabels({'10','20','30','40','50'});
 xlim([0,50.75]);
                                                                                                                                                                                                                                                                                                                                                                          
   red =  [0.75, 0, 0];
-  blue=[0,0,0.75];
-  green=[0,0.75,0];
+  blue=[0,0,1];
+  green=[0,0.25,0];
   white = [1,1,1];
  dark =  [0, 0, 0];
  lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');

### 2018-03-28 FlairResearch/NewWithCovertDidfailFlair.m
Checking up

@@ -75,8 +75,13 @@ ylabel('AnalysisTime (Seconds)','FontSize',32);
 xticks([10,20,30,40,50]);
 xticklabels({'10','20','30','40','50'});
 xlim([0,50.75]);
-                                                                                                                                                                                                                                                                                                                                                                         
-  red =  [0.75, 0, 0];
+                
+len = 5;
+red = [1, 0, 0];
+pink = [255, 192, 203]/255;
+colors = [linspace(red(1),pink(1),len)', linspace(red(2),pink(2),len)', linspace(red(3),pink(3),len)'];
+
+  red1 =  [0.75, 0, 0];
   blue=[0,0,1];
   green=[0,0.25,0];
   white = [1,1,1];

### 2018-03-28 FlairResearch/PatternsPractice.m

@@ -1,0 +1,351 @@
+% Create original plot
+fH = gcf; colormap(jet(4));
+h = bar(rand(3, 4));
+legend('Apple', 'Orange', 'Banana', 'Melon', 'Location', 'EastOutside');
+
+
+% Apply Brandon's function
+tH = title('Brandon''s applyhatch');
+applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
+function A = makehatch_plus(hatch,n,m)
+%MAKEHATCH_PLUS Predefined hatch patterns
+%
+% Modification of MAKEHATCH to allow for selection of matrix size. Useful whe using 
+%   APPLYHATCH_PLUS with higher resolution output.
+%
+% input (optional) N    size of hatch matrix (default = 6)
+% input (optional) M    width of lines and dots in hatching (default = 1)
+%
+%  MAKEHATCH_PLUS(HATCH,N,M) returns a matrix with the hatch pattern for HATCH
+%   according to the following table:
+%      HATCH        pattern
+%     -------      ---------
+%        /          right-slanted lines
+%        \          left-slanted lines
+%        |          vertical lines
+%        -          horizontal lines
+%        +          crossing vertical and horizontal lines
+%        x          criss-crossing lines
+%        .          square dots
+%        c          circular dots
+%        w          Just a blank white pattern
+%        k          Just a totally black pattern
+%
+%  See also: APPLYHATCH, APPLYHATCH_PLUS, APPLYHATCH_PLUSCOLOR, MAKEHATCH
+
+%  By Ben Hinkle, bhinkle@mathworks.com
+%  This code is in the public domain. 
+
+% Modified Brian FG Katz    8-aout-03
+% Modified David M Kaplan    19-fevrier-08
+
+if ~exist('n','var'), n = 6; end
+if ~exist('m','var'), m = 1; end
+n=round(n);
+
+switch (hatch)
+  case '\'
+    [B,C] = meshgrid( 0:n-1 );
+    B = B-C; 
+    clear C
+    A = abs(B) <= m/2;
+    A = A | abs(B-n) <= m/2;
+    A = A | abs(B+n) <= m/2;
+  case '/'
+    A = fliplr(makehatch_plus('\',n,m));
+  case '|'
+    A=zeros(n);
+    A(:,1:m) = 1;
+  case '-'
+    A = makehatch_plus('|',n,m);
+    A = A';
+  case '+'
[…]

### 2018-03-29 FlairResearch/Paper.tex
Checking up
Did Matlab stuff

@@
 Each application from a given bundle was copied one by one into the input directory, and the tool was run after each application was copied.
-This resulted in each test for a given bundle and tool to have 50 total runs.
+This resulted in each test for a given bundle and tool having 50 total runs.
 The order in which the bundles were copied into the input directories of each tool remained constant allowing the times outputted to be compared directly.
@@
 Though it is not presented in \ref{figure:2}, Didfail fails to make it all the way to fifty applications.
-It could only get to thirty applications before failing to analyze any bundle that was larger.
-Flair maintains a near horizontal trend far below the other average times.\\
+It could only a bundle of thirty applications before failing.
+Flair maintains a near horizontal trend far below the other average times.
+This is due to its iterative analysis process.
+It has no need to analyze the whole bundle again, only the application that was added.\\
 
-		To assess the rate of failure in the various tools we used the methods described in \ref{methods} to find the percentage of applications in each test which failed.
+		To assess the rate of failure we used the methods described in \ref{methods} to find the percentage of applications in each test which failed.
 The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{32.19 percent\textbf{(NOT FINAL NUMBER)}} of applications on average across all runs.

### 2018-03-29 FlairResearch/BoxPlotGraphByTens.m

@@ -1,24 +1,28 @@
-Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
-Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
-Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
-SEALANT = xlsread('FlairResults.xlsx','SEALANT','K5:O54');
-DIALDroid = xlsread('FlairResults.xlsx','DIALDroid','L5:P54');
-itemNo = 250;
+Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
+Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
+Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
+SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
+DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
+itemNo = 30;
 %init Matrix
 datap = zeros(5,itemNo);
+disp(size(Covert));
+disp(Covert);
 for  n=1:5
-    for i=1:50
+    for i=1:6
+        disp((i-1)*5+1);
         %        Covert 1,6,11...
-        datap(n,(i-1)*5+1) = Covert(n,i);
+        datap(n,(i-1)*5+1) = Covert(i,n);
+        
         %        Flair 3,8,13...
-        datap(n,(i-1)*5+2) = Flair(n,i);
+        datap(n,(i-1)*5+2) = Flair(i,n);
         %       SEALANT 4,9,14
         datap(n,(i-1)*5+4) = SEALANT(i,n);
         %       DIALDroid 5,10,15
         datap(n,(i-1)*5+5) = DIALDroid(i,n);
-        if i<31
+        if i<4
            %        Didfail 2,7,12...
-            datap(n,(i-1)*5+3) = Didfail(n,i);
+            datap(n,(i-1)*5+3) = Didfail(i,n);
         else
             datap(n,(i-1)*5+3) = -105;
         end
@@ -56,7 +60,7 @@ end
  ax = gca;
  ax.FontSize = 19;
  
- ylim([-100 4000]);
+ ylim([-100 2500]);
  yt = get(gca,'YTick');
 %set(gca,'YTickLabel', sprintf('%.4f',yt))
[…]

### 2018-03-29 FlairResearch/PatternsPractice.m

@@ -3,349 +3,12 @@ fH = gcf; colormap(jet(4));
 h = bar(rand(3, 4));
 legend('Apple', 'Orange', 'Banana', 'Melon', 'Location', 'EastOutside');
 
-
 % Apply Brandon's function
-tH = title('Brandon''s applyhatch');
-applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
-function A = makehatch_plus(hatch,n,m)
-%MAKEHATCH_PLUS Predefined hatch patterns
-%
-% Modification of MAKEHATCH to allow for selection of matrix size. Useful whe using 
-%   APPLYHATCH_PLUS with higher resolution output.
-%
-% input (optional) N    size of hatch matrix (default = 6)
-% input (optional) M    width of lines and dots in hatching (default = 1)
-%
-%  MAKEHATCH_PLUS(HATCH,N,M) returns a matrix with the hatch pattern for HATCH
-%   according to the following table:
-%      HATCH        pattern
-%     -------      ---------
-%        /          right-slanted lines
-%        \          left-slanted lines
-%        |          vertical lines
-%        -          horizontal lines
-%        +          crossing vertical and horizontal lines
-%        x          criss-crossing lines
-%        .          square dots
-%        c          circular dots
-%        w          Just a blank white pattern
-%        k          Just a totally black pattern
-%
-%  See also: APPLYHATCH, APPLYHATCH_PLUS, APPLYHATCH_PLUSCOLOR, MAKEHATCH
+%tH = title('Brandon''s applyhatch');
+%applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
 
-%  By Ben Hinkle, bhinkle@mathworks.com
-%  This code is in the public domain. 
+% Apply Brian's function
+%set(tH, 'String', 'Brian''s applyhatch');
+applyhatch_plusC(fH, '\-x.', 'rkbk');
 
-% Modified Brian FG Katz    8-aout-03
-% Modified David M Kaplan    19-fevrier-08
-
-if ~exist('n','var'), n = 6; end
-if ~exist('m','var'), m = 1; end
-n=round(n);
-
-switch (hatch)
-  case '\'
-    [B,C] = meshgrid( 0:n-1 );
-    B = B-C; 
-    clear C
-    A = abs(B) <= m/2;
-    A = A | abs(B-n) <= m/2;
[…]

### 2018-03-29 FlairResearch/BoxPlotByTens_2.m
Changed the matlab stuff

@@ -1,0 +1,103 @@
+Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
+Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
+Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
+SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
+DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
+itemNo = 6;
+
+DialDroidData=zeros(5,itemNo);
+CovertData=zeros(5,itemNo);
+SEALANTData=zeros(5,itemNo);
+FlairData=zeros(5,itemNo);
+DidfailData=zeros(5,itemNo);
+
+for  n=1:5
+    for i=1:6
+        DialDroidData(n,i)=DIALDroid(i,n);
+        CovertData(n,i)=Covert(i,n);
+        FlairData(n,i)=Flair(i,n);
+        SEALANTData(n,i)=SEALANT(i,n);
+        if i<5
+         DidfailData(n,i)=Didfail(i,n);
+        else
+         DidfailData(n,i)=-105;
+        end
+    end
+end
+
+g=zeros(1,itemNo);
+posDialDroid = zeros(1,itemNo);
+posCovert = zeros(1,itemNo);
+posFlair = zeros(1,itemNo);
+posDidfail = zeros(1,itemNo);
+posSEALANT = zeros(1,itemNo);
+for i=1:itemNo
+    g(i)=i;
+    posDialDroid(i) = i+0.2;
+    posCovert(i) = i+0.1;
+    posFlair(i) = i-0.1;
+    posDidfail(i) = i-0.2;
+    posSEALANT(i) = i;
+end
+disp(size(posDialDroid));
+ DialDroidPlot=boxplot(DialDroidData,'positions',posDialDroid,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
+ hold on
+ CovertBoxPlot=boxplot(CovertData,'positions',posCovert,'whisker',5,'Widths',0.1);
+ hold on
+ FlairBoxPlot=boxplot(FlairData,'positions',posFlair,'whisker',5,'Widths',0.1);
+ hold on
+ DidfailBoxPlot=boxplot(DidfailData,'positions',posDidfail,'whisker',5,'Widths',0.1);
+ hold on
[…]

### 2018-03-29 FlairResearch/PatternsPractice.m

@@ -1,14 +1,16 @@
+addpath('applyhatch_plusC');
+addpath('applyhatch_pluscolor');
 % Create original plot
 fH = gcf; colormap(jet(4));
 h = bar(rand(3, 4));
 legend('Apple', 'Orange', 'Banana', 'Melon', 'Location', 'EastOutside');
 
 % Apply Brandon's function
-%tH = title('Brandon''s applyhatch');
-%applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
+tH = title('Brandon''s applyhatch');
+applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
 
 % Apply Brian's function
-%set(tH, 'String', 'Brian''s applyhatch');
-applyhatch_plusC(fH, '\-x.', 'rkbk');
+set(tH, 'String', 'Brian''s applyhatch');
+applyhatch_plusC(fH, '\-x.', 'kkkk');
 
 set(tH, 'String', 'Original');

### 2018-03-29 FlairResearch/hatch.m

@@ -1,0 +1,286 @@
+function  hatch(obj,angle,color,style,step,width)
+% HATCH  Hatches a two-dimensional domain.
+%     Somewhat similar to the FILL command but fills the closed
+%     contour with hatched lines instead of uniform color.
+%     The boundary line(s) must be created prior to this command
+%     and its handle(s) specified by OBJ argument.
+%   HATCH(OBJ) Hatchs the domain bounded by the Xdata and Ydata
+%     properties of the OBJ (can be line or patch type).
+%   HATCH by itself takes as OBJ the last object created in the 
+%     current axes.
+%   HATCH(OBJ,ANGLE,COLOR,STYLE,STEP,WIDTH) Specifies additional
+%     parameters:  slope of the hatches (in degrees),
+%     their color ([red green blue], or 'r','g','b','w','y','c','m')
+%     the linestyle ('-','--','-.',':') and also the steps
+%     (distances between hatches) and the linewidth (thickness)
+%     of the hatch lines (the last two in points).
+%     All arguments are optional but must be in the given order.
+%     They also can be grouped in two vectors for convenience:
+%   HATCH(OBJ,[ANGLE STEP WIDTH],[COLOR STYLE]), where the last 
+%     argument is a string: 'w--', '-.y' are both legal notations.
+%   LH = HATCH(OBJ) also returns the handle of a hatch line.
+%     OBJ can be a vector of several handles, in which case the
+%     composite boundary is hatched. If one contour lies within
+%     another, then the first one will appear as a "hole" in the 
+%     outer contour.
+%
+%     Examples:
+%   HATCH(L,30,[1 0 0],'--',8,2) or
+%   HATCH(L,[30 8 2],'r--')    Hatchs a domain
+%     bounded by the contour L with red dashed lines of 2-point
+%     thickness and 8-point steps, inclined at 30 degrees
+%     to the x-axis.
+%   HATCH([L1 L2],'CROSS')  Hatches the domain with composite
[…]

### 2018-03-30 FlairResearch/AveragesLineGraph.m
Finished up graphs

@@ -1,9 +1,9 @@
-X = xlsread('FlairResults.xlsx','Total Averages','A5:A54');
-CovertAverage=xlsread('FlairResults.xlsx','Total Averages','B5:B54');
-FlairAverage=xlsread('FlairResults.xlsx','Total Averages','D5:D54');
-SEALANTAverage=xlsread('FlairResults.xlsx','Total Averages','E5:E54');
-DIALDroidAverage=xlsread('FlairResults.xlsx','Total Averages','F5:F54');
-DidfailAverage=xlsread('FlairResults.xlsx','Total Averages','C5:C34');
+X = xlsread('Flair Reseach Results.xlsx','Total Averages','A5:A54');
+CovertAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','B5:B54');
+FlairAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','D5:D54');
+SEALANTAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','E5:E54');
+DIALDroidAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','F5:F54');
+DidfailAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','C5:C34');
 
 black=[0,0,0];
 darkgrey=[0.25,0.25,0.25];
@@ -28,4 +28,4 @@ xlabel('Bundle Size(#Apps)','FontSize',24);
 ylabel('AnalysisTime (Seconds)','FontSize',24);
 
 xlim([1,50]);
-ylim([-100,4000]);
+ylim([-100,2500]);

### 2018-03-30 FlairResearch/BoxPlotByTens_2.m

@@ -39,16 +39,16 @@ for i=1:itemNo
     posDidfail(i) = i-0.2;
     posSEALANT(i) = i;
 end
-disp(size(posDialDroid));
+
  DialDroidPlot=boxplot(DialDroidData,'positions',posDialDroid,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
  hold on
- CovertBoxPlot=boxplot(CovertData,'positions',posCovert,'whisker',5,'Widths',0.1);
+ CovertBoxPlot=boxplot(CovertData,'positions',posCovert,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
  hold on
- FlairBoxPlot=boxplot(FlairData,'positions',posFlair,'whisker',5,'Widths',0.1);
+ FlairBoxPlot=boxplot(FlairData,'positions',posFlair,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
  hold on
- DidfailBoxPlot=boxplot(DidfailData,'positions',posDidfail,'whisker',5,'Widths',0.1);
+ DidfailBoxPlot=boxplot(DidfailData,'positions',posDidfail,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
  hold on
- SEALANTBoxPlot=boxplot(SEALANTData,'positions',posSEALANT,'whisker',5,'Widths',0.1);
+ SEALANTBoxPlot=boxplot(SEALANTData,'positions',posSEALANT,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
 hold off
  
  
@@ -57,8 +57,7 @@ hold off
   dark=[0.25,0.25,0.25];
   white = [1,1,1];
  black =  [0, 0, 0];
- lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
- set(lines, 'Color', black, 'LineWidth', 1);
+
  
  h = findobj(gcf,'Tag','Box');
  disp(size(h));
@@ -72,20 +71,19 @@ hold off
            boxcolor = grey;
        elseif j>12 && j<19
            %Flair
-           boxcolor = dark;
-       elseif j>18 && j<25
-           %Didfail
            boxcolor = black;
-       else
+           
+       elseif j>18 && j<25
            %Covert
            boxcolor = light;
+       else
+           %DIALDroid
+           boxcolor = dark;
        end    
[…]

### 2018-03-30 FlairResearch/CovertBoxPlot.m

@@ -1,12 +1,12 @@
 %Read Data in
-Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
-itemNo=50;
+Covert = xlsread('Flair Reseach Results.xlsx','Covert','R17:V27');
+itemNo=11;
 %Transfer data into an array
 datap = zeros(5,itemNo);
 for  n=1:5
-    for i=1:50
+    for i=1:itemNo
         %        Covert 1,4,7...
-        datap(n,i) = Covert(n,i);        
+        datap(n,i) = Covert(i,n);        
     end
 end
 
@@ -23,12 +23,14 @@ end
  boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
  
  %Give some buffer on each side
- xlim([0,51]);
+ xlim([0,11.5]);
+ set(gca,'xtick',1:11);
+ set(gca,'xticklabel',{'1','5','10','15','20','25','30','35','40','45','50'});
  
 %Set labels
 xlabel('Bundle Size(#Apps)','FontSize',26);
 ylabel('AnalysisTime (Seconds)','FontSize',26);
-title('Covert Analysis','FontSize',32);
+%title('Covert Analysis','FontSize',32);
 
 %Set Y limits
 ylim([-100 2500]);

### 2018-03-30 FlairResearch/Paper.tex
Worked on paper

@@
 \usepackage{blindtext}
+\usepackage{xcolor}
+\usepackage{multirow}
+\usepackage{wasysym} %For checkbox
 
@@
 	\textbf{RQ1:} How does Flair compare to other inter-application communication analysis tools in respect to the amount of time it takes to analyze a bundle of applications?\\
-	\textbf{RQ2:} How accurately does Flair analyze privilege escalation vulnerabilities within applications when ran against a bundle of benchmark applications?\\
+	\textbf{RQ2:} How accurately does Flair analyze privilege escalation vulnerabilities within applications when run against a bundle of benchmark applications?\\
 	\textbf{RQ3:} How does Flair's accuracy in analyzing privilege escalations compare to other inter-application communication analysis tools?\\
@@
 \paragraph{•}
-	To test these questions we ran Flair four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
+	To test these questions we ran Flair against four other inter-application analysis tools: Covert, Didfail, SEALANT, and DIALDroid.
 We used seven bundles of popular applications presented in table 1, each with fifty applications, to answer RQ1.
+Each of these bundles contained different applications or applications in a different order than the other bundles.
 We then used two bundles of benchmark bundles also presented in table 1 to answer RQ2 and RQ3.
@@
 Each test outputted its times to a single CSV file and the times from all tests were then combined into a master spreadsheet.
-These times were translated into graphs and are presented later in this paper.\\
-	In addition to analyzing the time it took each tool to analyze the bundles.
+These times were translated into graphs and are presented later in this paper.
+All tests were run three times to increase the validity of our results.\\
 	 We also noticed that DIALDroid would fail to analyze some applications.
@@
 \paragraph{•}
-
-	\textbf{Here will go text explaining RQ3 procedure.}
-\paragraph{•}
-	\textbf{Here will go text explaining Question 4 procedure.}
+	To answer both RQ2 and RQ3 we used the benchmark bundles DroidBench 2.0 ICCTA-Branch, and ICC-Bench to analyze how well each tool is at detecting ICC vulnerabilities.
+We selected various applications from each bundles intended to represent a wide range of security vulnerabilties present in android.
+Each tool was run against each specific benchmark applications and it was then recorded whether or not the tool was able to detect the vulnerability present in the benchmark application.
+These results are presented in \c.p{Benchmark table}, later in this paper.
 
@@
 \subsection{Testing Environment}
-	All testing for Question 1 and RQ2 was done on virtual machines running within Oracle VirtualBox.
+	All testing for RQ11 and RQ2 was done on virtual machines running within Oracle VirtualBox.
 Each of these machines was running Ubuntu 16.04 and had 8 processing threads clocked at 2.28 Ghz.
-The memory varied due to the fact that each tool had differing memory requirements.
-For Covert, Didfail, and Flair the machine was given 3 GB of memory.
-SEALANT required more memory to run and was given 6 GB.
-DIALDroid, the most memory intensive, was given 14 GB.
-These memory amounts were established by examining how much memory was allocated for each tool.
-The tools were each run with an excess of memory avaliable and then it was observed how much memory they each used.
-The tools were then given the amount of memory that each was observed to have used.
+We intended to run each tool with 3 Gb of memory allocated to their respective VM.
+In our testing it became apparent that both SEALANT and DIALDroid were unable to run with only 3 Gb of memory, therefore we assigned each tool 14 Gb of memory as this was the minimum amount of memory both tools were able to run at.
+This is advantageous for these two tool.
+Nonetheless, the results in \c.f{Results section} show that they are not as efficient as Flair in terms of scale-ability and just as accurate in detecting vulnerabilities.
 \subsection{Threats to Validity}
@@
 
-\clearpage
-\newpage
-
 \subsection{Results}
 
-%Figure that represents the box plot graphs of all the Tools
-\begin{figure*}[!ht]
-
-\centering
-	\includegraphics[width=\linewidth]{BoxPlotGraph}
-	\label{figure:1}
-	\caption{Box plot graphs showing tool analysis times for various tools.}
-\end{figure*}
-
-	%Average Analysis Time Graph
-	\begin{figure}[H]
-		\includegraphics[width=\linewidth]{AverageGraph}
-		\label{figure:2}
-		\caption{Average analysis times for tools.}
-	\end{figure}
-
-	\subsection{RQ1:}
+	\subsubsection{RQ1:}
 		We first look to evaluate the analysis time of Flair in relation to Covert, DIALDroid, and SEALANT.
-The box plot graphs presented in Figure 1 show the spread of analysis times for each tool.
+The box plot graphs presented in Figure 1 show the spread of analysis times for each tool at various points in our incremental testing.
+Though, the graph shows increases in bundle size by ten(or five if we uses 5 different graphs), only one app was added at a time in our testing.
 This data is presented in accordance with Figure 2 which represents the average analysis time of all tests run for all tools.
-These results show that Flair has a much smaller spread of analysis time across bundles, and much faster analysis times when analyzing bundles in an iterative fashion.
-Flair is able to analyze each application added to a bundle far faster since it only has to analyze the one application that was added, whereas the other tools analyze the entire bundle plus an additional application.\\
-		It is shown in Figure 2 that SEALANT and Covert follow similar trends, except SEALANT shows much greater analysis times.
-This is most likely because SEALANT is built on top of Covert and runs Covert within its Analysis tool.
-In addition to Covert SEALANT also runs IC3 in its analyzer tool.
-The trend of covert is maintained in the data, but extra time is added with the addition of the IC3.
-DIALDroid follows a trend which appears to cause a great increase in time during the first few applications of a bundle.
-After those first few applications, DIALDroid increases at a much slower rate.
-Didfail's analysis times grows far faster than any of the other tools.
-Though it is not presented in \ref{figure:2}, Didfail fails to make it all the way to fifty applications.
-It could only a bundle of thirty applications before failing.
-Flair maintains a near horizontal trend far below the other average times.
-This is due to its iterative analysis process.
-It has no need to analyze the whole bundle again, only the application that was added.\\
-
+All of the tools show differing trends in average analysis time, spread of their analysis times, and symmetry of the analysis times at a given bundle size.
+\\
+		The data presented in \c.p{Average Lines graph} show that Flair maintains analysis times far below any of the other tools.
+Flair is able to do this since it does not have to re-analyze the entire bundle when another application is added.
+Unlike the other tools, Flair only analyzes the application that was added to the bundle, greatly decreasing analysis times.
+The other tools show much higher analysis times, with Didfail by far taking the longest to analyze bundles of applications.
+In addition, Didfail was unable to analyze bundles larger than 30 applications.
+Once 30 applications were reached, Didfail failed to produce any results from the analysis.
+Covert shows a steadily increasing trend of analysis times.
+Therefore, even though Covert forms the foundations for Flair, Flair is able to greatly reduce times analysis of bundles in an incremental environment.
+SEALANT and DIALDroid both maintain average analysis times that are greater than both Flair and Covert, but are far below those of Didfail.
+Even though they use far more resources than either Flair or Covert, they are unable to compete in scale-ability.\\
+		In \c.p{Box Plot Figure} we present the spread and symmetry of each tools analysis times at various points in the incremental testing.
+Each tool has a certian amount of variability presented in the IQR of their given box plots.
+Flair maintains the lowest amount of variability by far.
+Therefore, Flair's analysis times are able to more easily predicted than any of the other tools.
+Covert in particular shows an extremely large amount of variability in the IQRs of its box plots, particularly when the bundle sizes increase to being over thirty applications DIALDroid and SEALANT both maintain spreads that are lower than those of Covert or even Didfail, but are still far greater than the spreads for Flair.
+It is clear that Flair is far more consistant in its analysis of bundles, where the other tools become far less predictable when the bundle sizes increase.
+The symmetry of these tools also differs.
+SEALANT has very symmetrical data all the way through the testing.
+Covert maintains a similar level of symmetry in its analysis times.
+DIALDroid and Covert, on the other hand, have widely varying symmetries presented in their box plots.
+These tools tend to have their analysis times for various bundles skewed to the right, though Covert becomes more symmetrical as the bundle size increases.
+Didfail, like Covert, has data that skews to the right with smaller bundles, but trends towards being more symmetrical as the bundles sizes increase.//
 		To assess the rate of failure we used the methods described in \ref{methods} to find the percentage of applications in each test which failed.
-The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{32.19 percent\textbf{(NOT FINAL NUMBER)}} of applications on average across all runs.
+The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{28.54 percent} of applications on average across all runs.
 This was primarily because DIALDroid would attempt to allocate more than our allotted 14 GB of memory, which was more than twice that allocated to any of the other tools.
@@
 
-	\subsection{RQ3:}
-		text
-	\subsection{Question 4:}
-		text
+	\begin{table*}[hb]
+\definecolor{trueColor}{RGB}{98,152,61}
+\definecolor{falseColor}{RGB}{192,0,0}
+\newcommand{\tp}{\textbf{\normalsize{\textcolor{trueColor}{\CheckedBox}}}}
+\newcommand{\fp}{\normalsize{\textcolor{falseColor}{\XBox}}}
+\newcommand{\fn}{\normalsize{\textcolor{falseColor}{\Square}}}
+
+\definecolor{light-gray}{gray}{0.90}
+\definecolor{LightCyan}{rgb}{0.88,1,1}
+
+\scriptsize
+\centering
+	\vspace{+0.3cm}
+	%\caption{Comparison between \@name, DidFail, and AmanDroid.
+TP, FP and FN are represented by symbols \tp, \fp, \fn, respectively.
+(X\#) indicates the number \# of detected instances for the corresponding symbol X.
+	%\label{table_comparison}}
+	\begin{tabular}{|p{0.07cm}|l|l|l|l|l|p{0.8cm}|}
+		\hline
+		& Test Case & DidFail & SEALANT &  DIALDroid & Covert & Flair \\ %DroidGuard \\
+		\hline
+		\hline
+		%\multicolumn{7}{|c|}{\cellcolor{light-gray}DroidBench2}\\\hline
+		\parbox[t]{2mm}{\multirow{23}{*}{\rotatebox[origin=c]{90}{DroidBench2}}}
+		%\parbox[t]{2mm}{\multirow{16}{*}{\rotatebox[origin=c]{90}{IPC}}}
+		&ICC\_bindService1    &\fp \fn &\tp &\tp	 &\tp	&\tp		\\
+		&ICC\_bindService2    &\fn &\tp	&\fn &\tp &\tp			\\
+		&ICC\_bindService3    &\fn &\tp	&\fn &\tp &\tp			\\
+		&ICC\_bindService4    &\fp \scriptsize (\fn \scriptsize 2)	&(\tp \scriptsize 2) &\tp\fn &\scriptsize (\tp \scriptsize 2) &\scriptsize (\tp \scriptsize 2)	\\
+		&ICC\_sendBroadcast1  &\tp &\tp &\tp &\tp &\tp \\
+		&ICC\_startActivity1  &\fn &\fn &\tp &\tp &\tp \\
+		&ICC\_startActivity2  &\fn	&\tp	&\tp	&\tp &\tp \\
+		&ICC\_startActivity3  &\fn	&\tp	&\tp	&\tp &\tp \\
+		&ICC\_startActivity4  &\fp	&	&\fn &	& 	\\
+		&ICC\_startActivity5  &\scriptsize (\fp \scriptsize 2)	&\fn	&\fn\ & &	\\
+		&ICC\_startActivityForResult1 	&\fn	&\tp &\tp &\tp	&\tp\\
+		&ICC\_startActivityForResult2 &\fn &\tp &\tp &\tp &\tp\\
+		&ICC\_startActivityForResult3 &\fn &\t- &\fn	&\tp	&\tp\\
+		&ICC\_startActivityForResult4 &\scriptsize (\fn \scriptsize 2)	&\tp\fn	&\tp\fn  & \scriptsize (\tp \scriptsize 2)	& \scriptsize (\tp \scriptsize 2)\\
+		&ICC\_startService1   &\fp \tp &\fn &\tp	&\tp &\tp\\
+		&ICC\_startService2   &\fp \tp &\fn &\tp &\tp &\tp\\
+		%\cline{2-7}
+		%\parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{C.Provider}}}	
+		&ICC\_delete1		&\fn	&\fn &\fn 	&\tp	&\tp	\\
+		&ICC\_insert1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
+		&ICC\_query1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
+		&ICC\_update1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
+		%\cline{2-7}
+		%\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{IAC}}}	
+		&IAC\_startActivity1	 &\tp \fp &\fn &\fn	&\tp	&\tp\\
+		&IAC\_startService1  &\tp &\fn &\fn &\tp &\tp\\
+		&IAC\_sendBroadcast1 &\tp &\fn &\fn &\tp	&\tp\\
+		\hline
+		\parbox[t]{2mm}{\multirow{9}{*}{\rotatebox[origin=c]{90}{ICC-Bench}}}
+		%\multicolumn{7}{|c|}{ICC-Bench}\\\hline
+		&Explicit\_Src\_Sink &\fn &\fn &\tp &\tp &\tp\\		
+		&Implicit\_Action  &\tp &\fn &\tp & \tp &\tp\\
+		&Implicit\_Category  &\tp &\fn &\tp &\tp &\tp\\
+		&Implicit\_Data1 &\tp &\fn &\tp &\tp  &\tp\\
+		&Implicit\_Data2 &\tp &\fn &\tp &\tp  &\tp\\
+		&Implicit\_Mix1 &\tp &\tp &\tp &\tp  &\tp\\
+		&Implicit\_Mix2 &\tp &\fn &\tp &\tp  &\tp\\
+		&DynRegisteredReceiver1 &\fn &\fn &\tp &\fn &\fn\\ 	
+		&DynRegisteredReceiver2 &\fn &\fn &\tp &\fn &\fn\\ 			
+		\hline		
+		\multicolumn{2}{|l|}{\textbf{Precision}}& 55\%&XX\%&XX\%&100\%&100\%\\
+		\hline
+		\multicolumn{2}{|l|}{\textbf{Recall}}& 37\%&XX\%&XX\%&97\%&97\%\\
+		\hline
+		\multicolumn{2}{|l|}{\textbf{F-measure}}& 44\%&XX\%&XX\%&98\%&98\%\\
+		\hline
+		\hline
+\end{tabular}
+\end{table*}
+
+	\subsubsection{RQ2:}
+		To test Flair's accuracy in identifying ICC vulnerabilities in Android we used a selection of test applications from two benchmark bundles: DroidBench 2.0 ICCTA Branch and ICC-Bench.
+The results of these tests are shown in \c.p{Benchmarks Table}.
+These results that Flair is able to detect nearly all ICC vulnerabilties within these benchmark bundles.
+Flair is able to maintain a very high level of accuracy in detecting ICC vulnerabilities, while still greatly decreasing analysis time and variability.
+
+	\subsubsection{RQ3:}
+		We also ran the same benchmark applications against Didfail, SEALANT,DIALDroid, and Covert so that we could compare how Flair related to other tools.
+While Covert was able to maintain the same levels of accuracy as Flair, our results showed that the other tools were not as accurate at detecting ICC vulnerabilities.
+Though, DIALDroid was the able to detect the two vulnerabilities that Flair was unable to detect, DynRegisteredReciever1 and 2, it was unable to detect many of the other vulnerabilities that we tested for.
+In particular, DIALDroid struggled to detect all vulnerabilties when there were multiple present in a single application.
+On both ICC bindService4 and ICC startActivityForResult4 it detected on of the present vulnerabilties, but failed to address the other.
+SEALANT failed to detect many of the present in our tests, as did Didfail.
+Didfail also reported multiple false positives, whereas we did not notice any of the other tools reporting false positives.
+Overall, Flair and Covert present accurate and reliable analysis of benchmark applications, while Didfail, SEALANT, and DIALDroid struggle to report all of the vulnerabilties present in Android applications today.
 

### 2018-03-31 FlairResearch/AveragesLineGraph.m
Chart stuff

@@ -10,15 +10,15 @@ darkgrey=[0.25,0.25,0.25];
 grey=[0.5,0.5,0.5];
 lightgrey=[0.75,0.75,0.75];
 
-plot(X,CovertAverage,'Color',black);
+plot(DidfailAverage,'Color',lightgrey,'linewidth',2);
 hold on
-plot(X,FlairAverage,'Color',darkgrey);
+plot(X,SEALANTAverage,'--','Color',darkgrey,'linewidth',2);
 hold on
-plot(X,SEALANTAverage,'Color',grey);
+plot(X,DIALDroidAverage,'-.','Color',grey,'linewidth',2);
 hold on
-plot(X,DIALDroidAverage,'--','Color',darkgrey);
+plot(X,CovertAverage,':','Color',darkgrey,'linewidth',2);
 hold on
-plot(DidfailAverage,'-.','Color',grey);
+plot(X,FlairAverage,'-','Color',black,'linewidth',2);
 hold off
 
 legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
@@ -29,3 +29,6 @@ ylabel('AnalysisTime (Seconds)','FontSize',24);
 
 xlim([1,50]);
 ylim([-100,2500]);
+
+xt=get(gca,'XTick');
+set(gca,'FontSize',16);

### 2018-03-31 FlairResearch/Paper.tex
Changed the BoxPlot graphs and Average lines graphs, fixed the Benchmark table, and added stuff to paper about individual graphs.

@@
 SEALANT, Covert, Didfail, and Flair all were able to run without any memory issues with far less memory.
-Therefore, Flair is able to analyze applications as reliably in terms of failure rate as well as SEALANT, Covert, and Didfail, while analyzing applications more reliably than DIALDroid.
+Therefore, Flair is able to analyze applications as reliably in terms of failure rate as well as SEALANT, Covert, and Didfail, while analyzing applications more reliably than DIALDroid.\\
+		\paragraph{In case we use five different graphs:}
+		\subparagraph{Didfail Graph:} 
+		The box plots in \c.p{Didfail box plot graph} show the spread and symmetry of the time it took Didfail to analyze the seven different bundles of applications.
+Didfail's analysis tends to skew to the right, and overall is not very symmetrical.
+Also, Didfail has an increasing IQR spread as the size of the bundles increases.
+		\subparagraph{SEALANT Graph:}
+		\c.p{SEALANT box plot graph} shows the spread of analysis times for SEALANT across the seven bundles.
+SEALANT maintains a relatively consistent spread and IQR of analysis times as the sizes of bundles increases.
+SEALANT also have very symmetrical data.
+		\subparagraph{DIALDroid Graph:}
+		The box plot graph for DIALDroid is presented in \c.p{DIALDroid box plot graph}.
+This data shows that DIALDroid, like Didfail tends to have data that skews right, but DIALDroid's analysis times become slightly more symmetrical as the size of the bundles increase.
+The IQR, though, grows slightly as the bundle size increases, showing greater variability in analysis times.
+		\subparagraph{Covert Graph:}
+		\c.p{Covert Box plot graph} shows the box plot data for Covert's analysis times.
+This data shows that Covert's analysis times across our seven bundles was extremely skewed right when the bundles size was small, but then became increasingly symmetrical as the size of the bundle increased.
+The IQR and spread, though, started out small and grew considerably as the bundle size increased.
+It is apparent that as the bundles sizes increase Covert's analysis times become far more variable.
+		\subparagraph{Flair Graph:}
+		The data in \c.p{Flair box plot graph} shows the spread and symmetry information for Flair's analysis times.
+This data shows that Flair is able to maintain extremely low analysis times for increasing bundle sizes.
+This is due to its iterative process.
+Flair only has to analysis applications that are added to the bundle, not the whole bundle.
+This allows Flair to maintain analysis times far below the other tool.
+Flair also maintains lower IQR ranges, showing that Flair is more consistent overall.
 
@@
 	%\label{table_comparison}}
-	\begin{tabular}{|p{0.07cm}|l|l|l|l|l|p{0.8cm}|}
+	\begin{tabular}{|p{0.07cm}|l|l|l|l|l|p{1.3cm}|}
 		\hline
-		& Test Case & DidFail & SEALANT &  DIALDroid & Covert & Flair \\ %DroidGuard \\
+		& Test Case & Covert & DIALDroid &  Didfail & Flair & SEALANT \\ %DroidGuard \\
 		\hline
@@
 		%\parbox[t]{2mm}{\multirow{16}{*}{\rotatebox[origin=c]{90}{IPC}}}
-		&ICC\_bindService1    &\fp \fn &\tp &\tp	 &\tp	&\tp		\\
-		&ICC\_bindService2    &\fn &\tp	&\fn &\tp &\tp			\\
-		&ICC\_bindService3    &\fn &\tp	&\fn &\tp &\tp			\\
-		&ICC\_bindService4    &\fp \scriptsize (\fn \scriptsize 2)	&(\tp \scriptsize 2) &\tp\fn &\scriptsize (\tp \scriptsize 2) &\scriptsize (\tp \scriptsize 2)	\\
+		&ICC\_bindService1    &\tp &\tp &\fp \fn	 &\tp	&\tp		\\
+		&ICC\_bindService2    &\tp &\fn	&\fn &\tp &\tp			\\
+		&ICC\_bindService3    &\tp &\fn	&\fn &\tp &\tp			\\
+		&ICC\_bindService4    &\scriptsize (\tp \scriptsize 2)	&\tp \fn &\fp \scriptsize (\fn \scriptsize 2) &\scriptsize (\tp \scriptsize 2)	 &\scriptsize (\tp \scriptsize 2)	\\
 		&ICC\_sendBroadcast1  &\tp &\tp &\tp &\tp &\tp \\
-		&ICC\_startActivity1  &\fn &\fn &\tp &\tp &\tp \\
-		&ICC\_startActivity2  &\fn	&\tp	&\tp	&\tp &\tp \\
-		&ICC\_startActivity3  &\fn	&\tp	&\tp	&\tp &\tp \\
-		&ICC\_startActivity4  &\fp	&	&\fn &	& 	\\
-		&ICC\_startActivity5  &\scriptsize (\fp \scriptsize 2)	&\fn	&\fn\ & &	\\
-		&ICC\_startActivityForResult1 	&\fn	&\tp &\tp &\tp	&\tp\\
-		&ICC\_startActivityForResult2 &\fn &\tp &\tp &\tp &\tp\\
-		&ICC\_startActivityForResult3 &\fn &\t- &\fn	&\tp	&\tp\\
-		&ICC\_startActivityForResult4 &\scriptsize (\fn \scriptsize 2)	&\tp\fn	&\tp\fn  & \scriptsize (\tp \scriptsize 2)	& \scriptsize (\tp \scriptsize 2)\\
-		&ICC\_startService1   &\fp \tp &\fn &\tp	&\tp &\tp\\
-		&ICC\_startService2   &\fp \tp &\fn &\tp &\tp &\tp\\
+		&ICC\_startActivity1  &\tp &\tp &\fn &\tp &\fn \\
+		&ICC\_startActivity2  &\tp	&\tp	&\fn	&\tp &\tp \\
+		&ICC\_startActivity3  &\tp	&\tp	&\fn	&\tp &\tp \\
+		&ICC\_startActivity4  & 	&	&\fp &	& 	\\
+		&ICC\_startActivity5  &	&	&\scriptsize (\fp \scriptsize 2) & &	\\
+		&ICC\_startActivityForResult1 	&\tp	&\tp &\fn &\tp	&\tp\\
+		&ICC\_startActivityForResult2 &\tp &\tp &\fn &\tp &\tp\\
+		&ICC\_startActivityForResult3 &\tp &\fn &\fn	&\tp	&\tp\\
+		&ICC\_startActivityForResult4 &\scriptsize (\tp \scriptsize 2)	&\tp\fn	&\scriptsize (\fn \scriptsize 2)  &\scriptsize (\tp \scriptsize 2) &\tp\fn \\
+		&ICC\_startService1   &\tp &\tp &\fp\tp	&\tp &\fn\\
+		&ICC\_startService2   &\tp &\tp &\fp\tp &\tp &\fn\\
 		%\cline{2-7}
 		%\parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{C.Provider}}}	
-		&ICC\_delete1		&\fn	&\fn &\fn 	&\tp	&\tp	\\
-		&ICC\_insert1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
-		&ICC\_query1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
-		&ICC\_update1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
+		&ICC\_delete1		&\tp	&\fn &\fn 	&\tp	&\fn	\\
+		&ICC\_insert1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
+		&ICC\_query1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
+		&ICC\_update1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
 		%\cline{2-7}
 		%\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{IAC}}}	
-		&IAC\_startActivity1	 &\tp \fp &\fn &\fn	&\tp	&\tp\\
-		&IAC\_startService1  &\tp &\fn &\fn &\tp &\tp\\
-		&IAC\_sendBroadcast1 &\tp &\fn &\fn &\tp	&\tp\\
+		&IAC\_startActivity1	 &\tp &\fn &\fp\tp	&\tp	&\fn\\
+		&IAC\_startService1  &\tp &\fn &\tp &\tp &\fn\\
+		&IAC\_sendBroadcast1 &\tp &\fn &\tp &\tp	&\fn\\
 		\hline
@@
 		%\multicolumn{7}{|c|}{ICC-Bench}\\\hline
-		&Explicit\_Src\_Sink &\fn &\fn &\tp &\tp &\tp\\		
-		&Implicit\_Action  &\tp &\fn &\tp & \tp &\tp\\
-		&Implicit\_Category  &\tp &\fn &\tp &\tp &\tp\\
-		&Implicit\_Data1 &\tp &\fn &\tp &\tp  &\tp\\
-		&Implicit\_Data2 &\tp &\fn &\tp &\tp  &\tp\\
+		&Explicit\_Src\_Sink &\tp &\tp &\fn &\tp &\fn\\		
+		&Implicit\_Action  &\tp &\tp &\tp & \tp &\fn\\
+		&Implicit\_Category  &\tp &\tp &\tp &\tp &\fn\\
+		&Implicit\_Data1 &\tp &\tp &\tp &\tp  &\fn\\
+		&Implicit\_Data2 &\tp &\tp &\tp &\tp  &\fn\\
 		&Implicit\_Mix1 &\tp &\tp &\tp &\tp  &\tp\\
-		&Implicit\_Mix2 &\tp &\fn &\tp &\tp  &\tp\\
-		&DynRegisteredReceiver1 &\fn &\fn &\tp &\fn &\fn\\ 	
-		&DynRegisteredReceiver2 &\fn &\fn &\tp &\fn &\fn\\ 			
+		&Implicit\_Mix2 &\tp &\tp &\tp &\tp  &\fn\\
+		&DynRegisteredReceiver1 &\fn &\tp &\fn &\fn &\fn\\ 	
+		&DynRegisteredReceiver2 &\fn &\tp &\fn &\fn &\fn\\ 			
 		\hline		
-		\multicolumn{2}{|l|}{\textbf{Precision}}& 55\%&XX\%&XX\%&100\%&100\%\\
+		\multicolumn{2}{|l|}{\textbf{Precision}}& 100\%&XX\%&55\%&100\%&XX\%\\
 		\hline
-		\multicolumn{2}{|l|}{\textbf{Recall}}& 37\%&XX\%&XX\%&97\%&97\%\\
+		\multicolumn{2}{|l|}{\textbf{Recall}}& 97\%&XX\%&37\%&97\%&XX\%\\
 		\hline
-		\multicolumn{2}{|l|}{\textbf{F-measure}}& 44\%&XX\%&XX\%&98\%&98\%\\
+		\multicolumn{2}{|l|}{\textbf{F-measure}}& 98\%&XX\%&44\%&98\%&XX\%\\
 		\hline

### 2018-03-31 FlairResearch/BoxPlotByTens_2.m

@@ -85,14 +85,14 @@ hold off
    end
  
     j=zeros(5,1);
-   j(1)=patch(NaN,NaN,NaN,white);
-   j(2)=patch(NaN,NaN,NaN,grey);
+   j(1)=patch(NaN,NaN,NaN,grey);
+   j(2)=patch(NaN,NaN,NaN,white);
    j(3)=patch(NaN,NaN,NaN,dark);
-   j(4)=patch(NaN,NaN,NaN,black);
-   j(5)=patch(NaN,NaN,NaN,light);
+   j(4)=patch(NaN,NaN,NaN,light);
+   j(5)=patch(NaN,NaN,NaN,black);
    
     c = get(gca, 'Children');
-   hleg1 = legend(j,{'SEALANT','Didfail','DIALDroid', 'Flair','Covert'},'Location','NorthWest');
+   hleg1 = legend(j,{'Didfail','SEALANT','DIALDroid', 'Covert','Flair'},'Location','NorthWest');
    set(hleg1,'FontSize',25) 
    
    set(gca,'xtick',1:6);
@@ -100,6 +100,8 @@ hold off
     xlim([0.5,6.5]);
     
     ylim([-100,4000]);
+    xt=get(gca,'XTick');
+    set(gca,'FontSize',16);
     
  lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
  set(lines, 'Color', black, 'LineWidth', 1.5);

### 2018-03-31 FlairResearch/CovertBoxPlot.m

@@ -46,3 +46,6 @@ lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
            boxcolor = [0.25,0.25,0.25];    
      patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
    end
+
+xt=get(gca,'XTick');
+set(gca,'FontSize',16);

### 2018-03-31 FlairResearch/AveragesLineGraph.m
Added graphs with flair. Rearranged things.

@@ -1,34 +1,0 @@
-X = xlsread('Flair Reseach Results.xlsx','Total Averages','A5:A54');
-CovertAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','B5:B54');
-FlairAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','D5:D54');
-SEALANTAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','E5:E54');
-DIALDroidAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','F5:F54');
-DidfailAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','C5:C34');
-
-black=[0,0,0];
-darkgrey=[0.25,0.25,0.25];
-grey=[0.5,0.5,0.5];
-lightgrey=[0.75,0.75,0.75];
-
-plot(DidfailAverage,'Color',lightgrey,'linewidth',2);
-hold on
-plot(X,SEALANTAverage,'--','Color',darkgrey,'linewidth',2);
-hold on
-plot(X,DIALDroidAverage,'-.','Color',grey,'linewidth',2);
-hold on
-plot(X,CovertAverage,':','Color',darkgrey,'linewidth',2);
-hold on
-plot(X,FlairAverage,'-','Color',black,'linewidth',2);
-hold off
-
-legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
-
-%Set labels
-xlabel('Bundle Size(#Apps)','FontSize',24);
-ylabel('AnalysisTime (Seconds)','FontSize',24);
-
-xlim([1,50]);
-ylim([-100,2500]);
-
-xt=get(gca,'XTick');
-set(gca,'FontSize',16);

### 2018-03-31 FlairResearch/BoxPlotByTens_2.m

@@ -1,111 +1,0 @@
-Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
-Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
-Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
-SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
-DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
-itemNo = 6;
-
-DialDroidData=zeros(5,itemNo);
-CovertData=zeros(5,itemNo);
-SEALANTData=zeros(5,itemNo);
-FlairData=zeros(5,itemNo);
-DidfailData=zeros(5,itemNo);
-
-for  n=1:5
-    for i=1:6
-        DialDroidData(n,i)=DIALDroid(i,n);
-        CovertData(n,i)=Covert(i,n);
-        FlairData(n,i)=Flair(i,n);
-        SEALANTData(n,i)=SEALANT(i,n);
-        if i<5
-         DidfailData(n,i)=Didfail(i,n);
-        else
-         DidfailData(n,i)=-105;
-        end
-    end
-end
-
-g=zeros(1,itemNo);
-posDialDroid = zeros(1,itemNo);
-posCovert = zeros(1,itemNo);
-posFlair = zeros(1,itemNo);
-posDidfail = zeros(1,itemNo);
-posSEALANT = zeros(1,itemNo);
-for i=1:itemNo
-    g(i)=i;
-    posDialDroid(i) = i+0.2;
-    posCovert(i) = i+0.1;
-    posFlair(i) = i-0.1;
-    posDidfail(i) = i-0.2;
-    posSEALANT(i) = i;
-end
-
- DialDroidPlot=boxplot(DialDroidData,'positions',posDialDroid,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
- hold on
- CovertBoxPlot=boxplot(CovertData,'positions',posCovert,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
- hold on
- FlairBoxPlot=boxplot(FlairData,'positions',posFlair,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
- hold on
- DidfailBoxPlot=boxplot(DidfailData,'positions',posDidfail,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
- hold on
[…]

### 2018-03-31 FlairResearch/BoxPlotGraphByTens.m

@@ -1,127 +1,0 @@
-Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
-Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
-Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
-SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
-DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
-itemNo = 30;
-%init Matrix
-datap = zeros(5,itemNo);
-
-for  n=1:5
-    for i=1:6
-        %        Covert 1,6,11...
-        datap(n,(i-1)*5+1) = Covert(i,n);
-        
-        %        Flair 2,7,12...
-        datap(n,(i-1)*5+2) = Flair(i,n);
-        
-        %       SEALANT 4,9,14
-        datap(n,(i-1)*5+4) = SEALANT(i,n);
-        %       DIALDroid 5,10,15
-        datap(n,(i-1)*5+5) = DIALDroid(i,n);
-        if i<5
-           %        Didfail 3,8,13...
-            datap(n,(i-1)*5+3) = Didfail(i,n);
-        else
-            datap(n,(i-1)*5+3) = -105;
-        end
-        
-        
-    end
-end
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-    if mod(n1,5) == 1
-%        Covert 1,4,7...
-         pos(n1) = (n1-1)/5 + 1;
-    elseif mod(n1,5) == 2
-%        Didfail 2,5,8...
-        pos(n1) = (n1-2)/5+1 +0.6;
-    elseif mod(n1,5)==3
-        %        Flair 3,6,9...
-        pos(n1) =(n1-3)/5 + 0.7;
-    elseif mod(n1,5)==4
-        %       SEALANT 4,9,14
-        pos(n1) =(n1-4)/5 + 0.8;
-    else
-        %       DIAlDroid 5,10,15
-        pos(n1) =n1/5 + 0.9;
-    end
-end
-
-%boxplot(datap,g,'positions',pos);
-
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.1);
- 
- % 
- 
- ax = gca;
- ax.FontSize = 19;
- 
- ylim([-100 2500]);
- yt = get(gca,'YTick');
[…]

### 2018-03-31 FlairResearch/CovertBoxPlot.m

@@ -1,51 +1,0 @@
-%Read Data in
-Covert = xlsread('Flair Reseach Results.xlsx','Covert','R17:V27');
-itemNo=11;
-%Transfer data into an array
-datap = zeros(5,itemNo);
-for  n=1:5
-    for i=1:itemNo
-        %        Covert 1,4,7...
-        datap(n,i) = Covert(i,n);        
-    end
-end
-
-%Get the x axis positions and put them into the array
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-%        Covert 1,4,7...
-         pos(n1) = n1;
-end
-
-%Plot the data into the box plot
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
- 
- %Give some buffer on each side
- xlim([0,11.5]);
- set(gca,'xtick',1:11);
- set(gca,'xticklabel',{'1','5','10','15','20','25','30','35','40','45','50'});
- 
-%Set labels
-xlabel('Bundle Size(#Apps)','FontSize',26);
-ylabel('AnalysisTime (Seconds)','FontSize',26);
-%title('Covert Analysis','FontSize',32);
-
-%Set Y limits
-ylim([-100 2500]);
-yt = get(gca,'YTick');
-
-%Gets the plots
-lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
- set(lines, 'Color', 'k');
-%  Change Box Color
-  h = findobj(gca,'Tag','Box');
-   for j=1:length(h)
-       x = mod(j,3);
-           boxcolor = [0.25,0.25,0.25];    
-     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
-   end
-
-xt=get(gca,'XTick');
-set(gca,'FontSize',16);

### 2018-03-31 FlairResearch/DIALDroidBoxPlots.m

@@ -1,46 +1,0 @@
-%Read Data in
-Flair = xlsread('FlairResults.xlsx','DIALDroid','L5:P54');
-itemNo=50;
-%Transfer data into an array
-datap = zeros(5,itemNo);
-for  n=1:5
-    for i=1:50
-        %        Covert 1,4,7...
-        datap(n,i) = Flair(i,n);        
-    end
-end
-
-%Get the x axis positions and put them into the array
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-%        Covert 1,4,7...
-         pos(n1) = n1;
-end
-
-%Plot the data into the box plot
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
- 
- %Give some buffer on each side
- xlim([0,51]);
- 
-%Set labels
-xlabel('Bundle Size(#Apps)','FontSize',26);
-ylabel('AnalysisTime (Seconds)','FontSize',26);
-title('DIALDroid Analysis','FontSize',32);
-
-%Set Y limits
-ylim([-100 2500]);
-yt = get(gca,'YTick');
-
-%Gets the plots
-lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
- set(lines, 'Color', 'k');
-%  Change Box Color
-  h = findobj(gca,'Tag','Box');
-   for j=1:length(h)
-       x = mod(j,3);
-           boxcolor = [0.25,0.25,0.25];    
-     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
-   end

### 2018-03-31 FlairResearch/DidfailBoxPlot.m

@@ -1,45 +1,0 @@
-%Read Data in
-Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
-itemNo=30;
-%Transfer data into an array
-datap = zeros(5,itemNo);
-for  n=1:5
-    for i=1:itemNo
-        datap(n,i) = Didfail(n,i);        
-    end
-end
-
-%Get the x axis positions and put them into the array
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-%        Covert 1,4,7...
-         pos(n1) = n1;
-end
-
-%Plot the data into the box plot
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
- 
- %Give some buffer on each side
- xlim([0,31]);
- 
-%Set labels
-xlabel('Bundle Size(#Apps)','FontSize',26);
-ylabel('AnalysisTime (Seconds)','FontSize',26);
-title('Didfail Analysis','FontSize',32);
-
-%Set Y limits
-ylim([-100 2500]);
-yt = get(gca,'YTick');
-
-%Gets the plots
-lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
- set(lines, 'Color', 'k');
-%  Change Box Color
-  h = findobj(gca,'Tag','Box');
-   for j=1:length(h)
-       x = mod(j,3);
-           boxcolor = [0.25,0.25,0.25];    
-     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
-   end

### 2018-03-31 FlairResearch/FlairBoxPlot.m

@@ -1,46 +1,0 @@
-%Read Data in
-Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
-itemNo=50;
-%Transfer data into an array
-datap = zeros(5,itemNo);
-for  n=1:5
-    for i=1:50
-        %        Covert 1,4,7...
-        datap(n,i) = Flair(n,i);        
-    end
-end
-
-%Get the x axis positions and put them into the array
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-%        Covert 1,4,7...
-         pos(n1) = n1;
-end
-
-%Plot the data into the box plot
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
- 
- %Give some buffer on each side
- xlim([0,51]);
- 
-%Set labels
-xlabel('Bundle Size(#Apps)','FontSize',26);
-ylabel('AnalysisTime (Seconds)','FontSize',26);
-title('Flair Analysis','FontSize',32);
-
-%Set Y limits
-ylim([-100 2500]);
-yt = get(gca,'YTick');
-
-%Gets the plots
-lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
- set(lines, 'Color', 'k');
-%  Change Box Color
-  h = findobj(gca,'Tag','Box');
-   for j=1:length(h)
-       x = mod(j,3);
-           boxcolor = [0.25,0.25,0.25];    
-     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
-   end

### 2018-03-31 FlairResearch/LineGraphs.m

@@ -1,12 +1,0 @@
-Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
-X=5;
-
-Y=zeros(50,5);
-
-for  n=1:5
-    for i=1:50
-        Y(i,n)=Covert(n,i);
-    end
-end
-
-plot(Y);

### 2018-03-31 FlairResearch/MatLabSource/AveragesLineGraph.m

@@ -1,0 +1,34 @@
+X = xlsread('Flair Reseach Results.xlsx','Total Averages','A5:A54');
+CovertAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','B5:B54');
+FlairAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','D5:D54');
+SEALANTAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','E5:E54');
+DIALDroidAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','F5:F54');
+DidfailAverage=xlsread('Flair Reseach Results.xlsx','Total Averages','C5:C34');
+
+black=[0,0,0];
+darkgrey=[0.25,0.25,0.25];
+grey=[0.5,0.5,0.5];
+lightgrey=[0.75,0.75,0.75];
+
+plot(DidfailAverage,'Color',lightgrey,'linewidth',2);
+hold on
+plot(X,SEALANTAverage,'--','Color',darkgrey,'linewidth',2);
+hold on
+plot(X,DIALDroidAverage,'-.','Color',grey,'linewidth',2);
+hold on
+plot(X,CovertAverage,':','Color',darkgrey,'linewidth',2);
+hold on
+plot(X,FlairAverage,'-','Color',black,'linewidth',2);
+hold off
+
+legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
+
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',24);
+ylabel('AnalysisTime (Seconds)','FontSize',24);
+
+xlim([1,50]);
+ylim([-100,2500]);
+
+xt=get(gca,'XTick');
+set(gca,'FontSize',16);

### 2018-03-31 FlairResearch/MatLabSource/BoxPlotByTens_2.m

@@ -1,0 +1,111 @@
+Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
+Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
+Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
+SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
+DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
+itemNo = 6;
+
+DialDroidData=zeros(5,itemNo);
+CovertData=zeros(5,itemNo);
+SEALANTData=zeros(5,itemNo);
+FlairData=zeros(5,itemNo);
+DidfailData=zeros(5,itemNo);
+
+for  n=1:5
+    for i=1:6
+        DialDroidData(n,i)=DIALDroid(i,n);
+        CovertData(n,i)=Covert(i,n);
+        FlairData(n,i)=Flair(i,n);
+        SEALANTData(n,i)=SEALANT(i,n);
+        if i<5
+         DidfailData(n,i)=Didfail(i,n);
+        else
+         DidfailData(n,i)=-105;
+        end
+    end
+end
+
+g=zeros(1,itemNo);
+posDialDroid = zeros(1,itemNo);
+posCovert = zeros(1,itemNo);
+posFlair = zeros(1,itemNo);
+posDidfail = zeros(1,itemNo);
+posSEALANT = zeros(1,itemNo);
+for i=1:itemNo
+    g(i)=i;
+    posDialDroid(i) = i+0.2;
+    posCovert(i) = i+0.1;
+    posFlair(i) = i-0.1;
+    posDidfail(i) = i-0.2;
+    posSEALANT(i) = i;
+end
+
+ DialDroidPlot=boxplot(DialDroidData,'positions',posDialDroid,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
+ hold on
+ CovertBoxPlot=boxplot(CovertData,'positions',posCovert,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
+ hold on
+ FlairBoxPlot=boxplot(FlairData,'positions',posFlair,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
+ hold on
+ DidfailBoxPlot=boxplot(DidfailData,'positions',posDidfail,'whisker',5,'Widths',0.1,'Colors',[0 0 0]);
+ hold on
[…]

### 2018-03-31 FlairResearch/MatLabSource/BoxPlotGraphByTens.m

@@ -1,0 +1,127 @@
+Covert = xlsread('Flair Reseach Results.xlsx','Covert','R5:V10');
+Flair = xlsread('Flair Reseach Results.xlsx','Flair','R5:V10');
+Didfail = xlsread('Flair Reseach Results.xlsx','Didfail','P5:T8');
+SEALANT = xlsread('Flair Reseach Results.xlsx','SEALANT','R5:V10');
+DIALDroid = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB5:AF10');
+itemNo = 30;
+%init Matrix
+datap = zeros(5,itemNo);
+
+for  n=1:5
+    for i=1:6
+        %        Covert 1,6,11...
+        datap(n,(i-1)*5+1) = Covert(i,n);
+        
+        %        Flair 2,7,12...
+        datap(n,(i-1)*5+2) = Flair(i,n);
+        
+        %       SEALANT 4,9,14
+        datap(n,(i-1)*5+4) = SEALANT(i,n);
+        %       DIALDroid 5,10,15
+        datap(n,(i-1)*5+5) = DIALDroid(i,n);
+        if i<5
+           %        Didfail 3,8,13...
+            datap(n,(i-1)*5+3) = Didfail(i,n);
+        else
+            datap(n,(i-1)*5+3) = -105;
+        end
+        
+        
+    end
+end
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+    if mod(n1,5) == 1
+%        Covert 1,4,7...
+         pos(n1) = (n1-1)/5 + 1;
+    elseif mod(n1,5) == 2
+%        Didfail 2,5,8...
+        pos(n1) = (n1-2)/5+1 +0.6;
+    elseif mod(n1,5)==3
+        %        Flair 3,6,9...
+        pos(n1) =(n1-3)/5 + 0.7;
+    elseif mod(n1,5)==4
+        %       SEALANT 4,9,14
+        pos(n1) =(n1-4)/5 + 0.8;
+    else
+        %       DIAlDroid 5,10,15
+        pos(n1) =n1/5 + 0.9;
+    end
+end
+
+%boxplot(datap,g,'positions',pos);
+
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.1);
+ 
+ % 
+ 
+ ax = gca;
+ ax.FontSize = 19;
+ 
+ ylim([-100 2500]);
[…]

### 2018-03-31 FlairResearch/MatLabSource/CovertBoxPlot.m

@@ -1,0 +1,75 @@
+%Read Data in
+Covert = xlsread('Flair Reseach Results.xlsx','DIALDroid','AB17:AF27');
+Flair = xlsread('Flair Reseach Results.xlsx','Flair','R17:V27');
+itemNo=11;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+datap1 = zeros(5,itemNo);
+for  n=1:5
+    for i=1:itemNo
+        %        Covert 1,4,7...
+        
+        datap(n,i) = Covert(i,n); 
+        
+        datap1(n,i) = Flair(i,n);
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0,0,0]);
+ hold on
+ boxplot(datap1,g,'positions',pos-0.275,'whisker',5,'Widths',0.26,'Color',[0,0,0]);
+ hold off
+ 
+ %Give some buffer on each side
+ xlim([0,11.5]);
+ set(gca,'xtick',1:11);
+ set(gca,'xticklabel',{'1','5','10','15','20','25','30','35','40','45','50'});
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+%title('Covert Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 2500]);
+yt = get(gca,'YTick');
+
+FlairColor=[0,0,0];
+OtherColor=[0.25,0.25,0.25];
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+        if j>11
+           boxcolor = OtherColor; 
+           patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+        else
+           boxcolor = FlairColor;
[…]

### 2018-03-31 FlairResearch/MatLabSource/DIALDroidBoxPlots.m

@@ -1,0 +1,46 @@
+%Read Data in
+Flair = xlsread('FlairResults.xlsx','DIALDroid','L5:P54');
+itemNo=50;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,i) = Flair(i,n);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,51]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('DIALDroid Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 2500]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-31 FlairResearch/MatLabSource/DidfailBoxPlot.m

@@ -1,0 +1,45 @@
+%Read Data in
+Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
+itemNo=30;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:itemNo
+        datap(n,i) = Didfail(n,i);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,31]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Didfail Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 2500]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-31 FlairResearch/MatLabSource/FlairBoxPlot.m

@@ -1,0 +1,46 @@
+%Read Data in
+Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
+itemNo=50;
+%Transfer data into an array
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,4,7...
+        datap(n,i) = Flair(n,i);        
+    end
+end
+
+%Get the x axis positions and put them into the array
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+%        Covert 1,4,7...
+         pos(n1) = n1;
+end
+
+%Plot the data into the box plot
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.26,'Color',[0.25,0.25,0.25]);
+ 
+ %Give some buffer on each side
+ xlim([0,51]);
+ 
+%Set labels
+xlabel('Bundle Size(#Apps)','FontSize',26);
+ylabel('AnalysisTime (Seconds)','FontSize',26);
+title('Flair Analysis','FontSize',32);
+
+%Set Y limits
+ylim([-100 2500]);
+yt = get(gca,'YTick');
+
+%Gets the plots
+lines = findobj(gcf, 'type', 'line', 'Tag', 'Median');
+ set(lines, 'Color', 'k');
+%  Change Box Color
+  h = findobj(gca,'Tag','Box');
+   for j=1:length(h)
+       x = mod(j,3);
+           boxcolor = [0.25,0.25,0.25];    
+     patch(get(h(j),'XData'),get(h(j),'YData'),boxcolor,'FaceAlpha',.5);
+   end

### 2018-03-31 FlairResearch/MatLabSource/LineGraphs.m

@@ -1,0 +1,12 @@
+Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
+X=5;
+
+Y=zeros(50,5);
+
+for  n=1:5
+    for i=1:50
+        Y(i,n)=Covert(n,i);
+    end
+end
+
+plot(Y);

### 2018-03-31 FlairResearch/MatLabSource/NewWithCovertDidfailFlair.m

@@ -1,0 +1,123 @@
+Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
+Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
+Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
+SEALANT = xlsread('FlairResults.xlsx','SEALANT','K5:O54');
+DIALDroid = xlsread('FlairResults.xlsx','DIALDroid','L5:P54');
+itemNo = 250;
+%init Matrix
+datap = zeros(5,itemNo);
+for  n=1:5
+    for i=1:50
+        %        Covert 1,6,11...
+        datap(n,(i-1)*5+1) = Covert(n,i);
+        %        Flair 3,8,13...
+        datap(n,(i-1)*5+2) = Flair(n,i);
+        %       SEALANT 4,9,14
+        datap(n,(i-1)*5+4) = SEALANT(i,n);
+        %       DIALDroid 5,10,15
+        datap(n,(i-1)*5+5) = DIALDroid(i,n);
+        if i<31
+           %        Didfail 2,7,12...
+            datap(n,(i-1)*5+3) = Didfail(n,i);
+        else
+            datap(n,(i-1)*5+3) = -105;
+        end
+        
+        
+    end
+end
+g = zeros(1,itemNo);
+pos = zeros(1,itemNo);
+for  n1=1:itemNo
+    g(n1) = n1;
+    if mod(n1,5) == 1
+%        Covert 1,4,7...
+         pos(n1) = (n1-1)/5 + 1;
+    elseif mod(n1,5) == 2
+%        Didfail 2,5,8...
+        pos(n1) = (n1-2)/5+1 +0.2;
+    elseif mod(n1,5)==3
+        %        Flair 3,6,9...
+        pos(n1) =(n1-3)/5 + 0.4;
+    elseif mod(n1,5)==4
+        %       SEALANT 4,9,14
+        pos(n1) =(n1-4)/5 + 0.6;
+    else
+        %       DIAlDroid 5,10,15
+        pos(n1) =n1/5 + 0.8;
+    end
+end
+
+%boxplot(datap,g,'positions',pos);
+
+ boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.2);
+ % 
+ 
+ ax = gca;
+ ax.FontSize = 19;
+ 
+ ylim([-100 4000]);
+ yt = get(gca,'YTick');
[…]

### 2018-03-31 FlairResearch/MatLabSource/PatternsPractice.m

@@ -1,0 +1,16 @@
+addpath('applyhatch_plusC');
+addpath('applyhatch_pluscolor');
+% Create original plot
+fH = gcf; colormap(jet(4));
+h = bar(rand(3, 4));
+legend('Apple', 'Orange', 'Banana', 'Melon', 'Location', 'EastOutside');
+
+% Apply Brandon's function
+tH = title('Brandon''s applyhatch');
+applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
+
+% Apply Brian's function
+set(tH, 'String', 'Brian''s applyhatch');
+applyhatch_plusC(fH, '\-x.', 'kkkk');
+
+set(tH, 'String', 'Original');

### 2018-03-31 FlairResearch/MatLabSource/practice.m

@@ -1,0 +1,3 @@
+h=bar(ones(2,2)) 
+hp = findobj(h,'type','patch'); 
+hatch(hp,45,'k','-',4,2);

### 2018-03-31 FlairResearch/NewWithCovertDidfailFlair.m

@@ -1,123 +1,0 @@
-Covert = xlsread('ResultOfCovertNew.xlsx','Covert50','I6:BF10');
-Flair = xlsread('ResultOfCovertNew.xlsx','Flair50','I6:BF10');
-Didfail = xlsread('ResultOfCovertNew.xlsx','Didfail50','I6:BF10');
-SEALANT = xlsread('FlairResults.xlsx','SEALANT','K5:O54');
-DIALDroid = xlsread('FlairResults.xlsx','DIALDroid','L5:P54');
-itemNo = 250;
-%init Matrix
-datap = zeros(5,itemNo);
-for  n=1:5
-    for i=1:50
-        %        Covert 1,6,11...
-        datap(n,(i-1)*5+1) = Covert(n,i);
-        %        Flair 3,8,13...
-        datap(n,(i-1)*5+2) = Flair(n,i);
-        %       SEALANT 4,9,14
-        datap(n,(i-1)*5+4) = SEALANT(i,n);
-        %       DIALDroid 5,10,15
-        datap(n,(i-1)*5+5) = DIALDroid(i,n);
-        if i<31
-           %        Didfail 2,7,12...
-            datap(n,(i-1)*5+3) = Didfail(n,i);
-        else
-            datap(n,(i-1)*5+3) = -105;
-        end
-        
-        
-    end
-end
-g = zeros(1,itemNo);
-pos = zeros(1,itemNo);
-for  n1=1:itemNo
-    g(n1) = n1;
-    if mod(n1,5) == 1
-%        Covert 1,4,7...
-         pos(n1) = (n1-1)/5 + 1;
-    elseif mod(n1,5) == 2
-%        Didfail 2,5,8...
-        pos(n1) = (n1-2)/5+1 +0.2;
-    elseif mod(n1,5)==3
-        %        Flair 3,6,9...
-        pos(n1) =(n1-3)/5 + 0.4;
-    elseif mod(n1,5)==4
-        %       SEALANT 4,9,14
-        pos(n1) =(n1-4)/5 + 0.6;
-    else
-        %       DIAlDroid 5,10,15
-        pos(n1) =n1/5 + 0.8;
-    end
-end
-
-%boxplot(datap,g,'positions',pos);
-
- boxplot(datap,g,'positions',pos,'whisker',5,'Widths',0.2);
- % 
- 
- ax = gca;
- ax.FontSize = 19;
- 
- ylim([-100 4000]);
[…]

### 2018-03-31 FlairResearch/PatternsPractice.m

@@ -1,16 +1,0 @@
-addpath('applyhatch_plusC');
-addpath('applyhatch_pluscolor');
-% Create original plot
-fH = gcf; colormap(jet(4));
-h = bar(rand(3, 4));
-legend('Apple', 'Orange', 'Banana', 'Melon', 'Location', 'EastOutside');
-
-% Apply Brandon's function
-tH = title('Brandon''s applyhatch');
-applyhatch_pluscolor(fH, '\-x.', 0, [1 0 1 0], jet(4));
-
-% Apply Brian's function
-set(tH, 'String', 'Brian''s applyhatch');
-applyhatch_plusC(fH, '\-x.', 'kkkk');
-
-set(tH, 'String', 'Original');

### 2018-03-31 FlairResearch/hatch.m

@@ -1,286 +1,0 @@
-function  hatch(obj,angle,color,style,step,width)
-% HATCH  Hatches a two-dimensional domain.
-%     Somewhat similar to the FILL command but fills the closed
-%     contour with hatched lines instead of uniform color.
-%     The boundary line(s) must be created prior to this command
-%     and its handle(s) specified by OBJ argument.
-%   HATCH(OBJ) Hatchs the domain bounded by the Xdata and Ydata
-%     properties of the OBJ (can be line or patch type).
-%   HATCH by itself takes as OBJ the last object created in the 
-%     current axes.
-%   HATCH(OBJ,ANGLE,COLOR,STYLE,STEP,WIDTH) Specifies additional
-%     parameters:  slope of the hatches (in degrees),
-%     their color ([red green blue], or 'r','g','b','w','y','c','m')
-%     the linestyle ('-','--','-.',':') and also the steps
-%     (distances between hatches) and the linewidth (thickness)
-%     of the hatch lines (the last two in points).
-%     All arguments are optional but must be in the given order.
-%     They also can be grouped in two vectors for convenience:
-%   HATCH(OBJ,[ANGLE STEP WIDTH],[COLOR STYLE]), where the last 
-%     argument is a string: 'w--', '-.y' are both legal notations.
-%   LH = HATCH(OBJ) also returns the handle of a hatch line.
-%     OBJ can be a vector of several handles, in which case the
-%     composite boundary is hatched. If one contour lies within
-%     another, then the first one will appear as a "hole" in the 
-%     outer contour.
-%
-%     Examples:
-%   HATCH(L,30,[1 0 0],'--',8,2) or
-%   HATCH(L,[30 8 2],'r--')    Hatchs a domain
-%     bounded by the contour L with red dashed lines of 2-point
-%     thickness and 8-point steps, inclined at 30 degrees
-%     to the x-axis.
-%   HATCH([L1 L2],'CROSS')  Hatches the domain with composite
[…]

### 2018-03-31 FlairResearch/practice.m

@@ -1,3 +1,0 @@
-h=bar(ones(2,2)) 
-hp = findobj(h,'type','patch'); 
-hatch(hp,45,'k','-',4,2);

### 2018-03-31 FlairResearch/MatLabSource/AveragesLineGraph.m
Fixed Average line graph legend.

@@ -21,14 +21,15 @@ hold on
 plot(X,FlairAverage,'-','Color',black,'linewidth',2);
 hold off
 
-legend({'Covert','Flair','SEALANT','DIALDroid','Didfail'},'Location','northwest','FontSize',14);
+hleg1=legend({'Didfail','SEALANT','DIALDroid','Covert','Flair'},'Location','northwest','FontSize',14);
+set(hleg1,'FontSize',25)
 
 %Set labels
 xlabel('Bundle Size(#Apps)','FontSize',24);
 ylabel('AnalysisTime (Seconds)','FontSize',24);
 
 xlim([1,50]);
-ylim([-100,2500]);
+ylim([-100,4000]);
 
 xt=get(gca,'XTick');
 set(gca,'FontSize',16);
